---
title: "moral language processing"
author: "Kobi Hackenburg"
date: "6/27/2021"
output: html_document
---
Set-up and load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load packages
library(quanteda)
library(quanteda.dictionaries)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(tidytext)
```
Step 0: Load all tweet data & construct corpora
```{r}
#2016 Dem primary
  #clinton
clinton2016primarytweets <- readLines("hillary2016tweets.txt")
clinton2016primary_corpus <- corpus(clinton2016primarytweets) 
clinton2016primary_corpus <- `docnames<-`(clinton2016primary_corpus, "clinton_2016primary")

  #sanders
sanders2016primarytweets <- readLines("bernie2016tweets.txt")
sanders2016primary_corpus <- corpus(sanders2016primarytweets) 
sanders2016primary_corpus <- `docnames<-`(sanders2016primary_corpus, "sanders_2016primary")

  #omalley
omalley2016primarytweets <- readLines("omalley2016tweets.txt")
omalley2016primary_corpus <- corpus(omalley2016primarytweets) 
omalley2016primary_corpus <- `docnames<-`(omalley2016primary_corpus, "omalley_2016primary")

#2016 Republican primary 
trump2016primarytweets <- readLines("trumptweets.txt")
trump_corpus <- corpus(trump2016primarytweets) 
trump_corpus <- `docnames<-`(trump_corpus, "trump_2016primary")

cruz2016primarytweets <- readLines("cruztweets.txt")
cruz_corpus <- corpus(cruz2016primarytweets) 
cruz_corpus <- `docnames<-`(cruz_corpus, "cruz_2016primary")

kasich2016primarytweets <- readLines("kasichtweets.txt")
kasich_corpus <- corpus(kasich2016primarytweets) 
kasich_corpus <- `docnames<-`(kasich_corpus, "kasich_2016primary")

rubio2016primarytweets <- readLines("rubiotweets.txt")
rubio_corpus <- corpus(rubio2016primarytweets) 
rubio_corpus <- `docnames<-`(rubio_corpus, "rubio_2016primary")

carson2016primarytweets <- readLines("carsontweets.txt")
carson_corpus <- corpus(carson2016primarytweets) 
carson_corpus <- `docnames<-`(carson_corpus, "carson_2016primary")

bush2016primarytweets <- readLines("bushtweets.txt")
bush_corpus <- corpus(bush2016primarytweets) 
bush_corpus <- `docnames<-`(bush_corpus, "bush_2016primary")

christie2016primarytweets <- readLines("christietweets.txt")
christie_corpus <- corpus(christie2016primarytweets) 
christie_corpus <- `docnames<-`(christie_corpus, "christie_2016primary")

paul2016primarytweets <- readLines("paultweets.txt")
paul_corpus <- corpus(paul2016primarytweets) 
paul_corpus <- `docnames<-`(paul_corpus, "paul_2016primary")

fiorina2016primarytweets <- readLines("fiorinatweets.txt")
fiorina_corpus <- corpus(fiorina2016primarytweets) 
fiorina_corpus <- `docnames<-`(fiorina_corpus, "fiorina_2016primary")

huckabee2016primarytweets <- readLines("huckabeetweets.txt")
huckabee_corpus <- corpus(huckabee2016primarytweets) 
huckabee_corpus <- `docnames<-`(huckabee_corpus, "huckabee_2016primary")

walker2016primarytweets <- readLines("walkertweets.txt")
walker_corpus <- corpus(walker2016primarytweets) 
walker_corpus <- `docnames<-`(walker_corpus, "walker_2016primary")

graham2016primarytweets <- readLines("grahamtweets.txt")
graham_corpus <- corpus(graham2016primarytweets) 
graham_corpus <- `docnames<-`(graham_corpus, "graham_2016primary")

jindal2016primarytweets <- readLines("jindaltweets.txt")
jindal_corpus <- corpus(jindal2016primarytweets) 
jindal_corpus <- `docnames<-`(jindal_corpus, "jindal_2016primary")

santorum2016primarytweets <- readLines("santorumtweets.txt")
santorum_corpus <- corpus(santorum2016primarytweets) 
santorum_corpus <- `docnames<-`(santorum_corpus, "santorum_2016primary")

pataki2016primarytweets <- readLines("patakitweets.txt")
pataki_corpus <- corpus(pataki2016primarytweets) 
pataki_corpus <- `docnames<-`(pataki_corpus, "pataki_2016primary")

perry2016primarytweets <- readLines("perrytweets.txt")
perry_corpus <- corpus(perry2016primarytweets) 
perry_corpus <- `docnames<-`(perry_corpus, "perry_2016primary")

#2020 Dem primary
biden2016primarytweets <- readLines("bidentweets.txt")
biden_corpus <- corpus(biden2016primarytweets) 
biden_corpus <- `docnames<-`(biden_corpus, "biden_2020primary")

sanders2016primarytweets <- readLines("sanderstweets.txt")
sanders_corpus <- corpus(sanders2016primarytweets) 
sanders_corpus <- `docnames<-`(sanders_corpus, "sanders_2020primary")

warren2016primarytweets <- readLines("warrentweets.txt")
warren_corpus <- corpus(warren2016primarytweets) 
warren_corpus <- `docnames<-`(warren_corpus, "warren_2020primary")

buttigieg2016primarytweets <- readLines("buttigiegtweets.txt")
buttigieg_corpus <- corpus(buttigieg2016primarytweets) 
buttigieg_corpus <- `docnames<-`(buttigieg_corpus, "buttigieg_2020primary")

klobuchar2016primarytweets <- readLines("klobuchartweets.txt")
klobuchar_corpus <- corpus(klobuchar2016primarytweets) 
klobuchar_corpus <- `docnames<-`(klobuchar_corpus, "klobuchar_2020primary")

steyer2016primarytweets <- readLines("steyertweets.txt")
steyer_corpus <- corpus(steyer2016primarytweets) 
steyer_corpus <- `docnames<-`(steyer_corpus, "steyer_2020primary")

yang2016primarytweets <- readLines("yangtweets.txt")
yang_corpus <- corpus(yang2016primarytweets) 
yang_corpus <- `docnames<-`(yang_corpus, "yang_2020primary")

harris2016primarytweets <- readLines("harristweets.txt")
harris_corpus <- corpus(harris2016primarytweets) 
harris_corpus <- `docnames<-`(harris_corpus, "harris_2020primary")

booker2016primarytweets <- readLines("bookertweets.txt")
booker_corpus <- corpus(booker2016primarytweets) 
booker_corpus <- `docnames<-`(booker_corpus, "booker_2020primary")

gabbard2016primarytweets <- readLines("gabbardtweets.txt")
gabbard_corpus <- corpus(gabbard2016primarytweets) 
gabbard_corpus <- `docnames<-`(gabbard_corpus, "gabbard_2020primary")

castro2016primarytweets <- readLines("castrotweets.txt")
castro_corpus <- corpus(castro2016primarytweets) 
castro_corpus <- `docnames<-`(castro_corpus, "castro_2020primary")

orourke2016primarytweets <- readLines("orourketweets.txt")
orourke_corpus <- corpus(orourke2016primarytweets) 
orourke_corpus <- `docnames<-`(orourke_corpus, "orourke_2020primary")

bloomberg2016primarytweets <- readLines("bloombergtweets.txt")
bloomberg_corpus <- corpus(bloomberg2016primarytweets) 
bloomberg_corpus <- `docnames<-`(bloomberg_corpus, "bloomberg_2020primary")

bennet2016primarytweets <- readLines("bennettweets.txt")
bennet_corpus <- corpus(bennet2016primarytweets) 
bennet_corpus <- `docnames<-`(bennet_corpus, "bennet_2020primary")

delaney2016primarytweets <- readLines("delaneytweets.txt")
delaney_corpus <- corpus(delaney2016primarytweets) 
delaney_corpus <- `docnames<-`(delaney_corpus, "delaney_2020primary")

williamson2016primarytweets <- readLines("williamsontweets.txt")
williamson_corpus <- corpus(williamson2016primarytweets) 
williamson_corpus <- `docnames<-`(williamson_corpus, "williamson_2020primary")

ryan2016primarytweets <- readLines("ryantweets.txt")
ryan_corpus <- corpus(ryan2016primarytweets) 
ryan_corpus <- `docnames<-`(ryan_corpus, "ryan_2020primary")

deblasio2016primarytweets <- readLines("deblasiotweets.txt")
deblasio_corpus <- corpus(deblasio2016primarytweets) 
deblasio_corpus <- `docnames<-`(deblasio_corpus, "deblasio_2020primary")

gillibrand2016primarytweets <- readLines("gillibrandtweets.txt")
gillibrand_corpus <- corpus(gillibrand2016primarytweets) 
gillibrand_corpus <- `docnames<-`(gillibrand_corpus, "gillibrand_2020primary")

inslee2016primarytweets <- readLines("insleetweets.txt")
inslee_corpus <- corpus(inslee2016primarytweets) 
inslee_corpus <- `docnames<-`(inslee_corpus, "inslee_2020primary")

hickenlooper2016primarytweets <- readLines("hickenloopertweets.txt")
hickenlooper_corpus <- corpus(hickenlooper2016primarytweets) 
hickenlooper_corpus <- `docnames<-`(hickenlooper_corpus, "hickenlooper_2020primary")

bullock2016primarytweets <- readLines("bullocktweets.txt")
bullock_corpus <- corpus(bullock2016primarytweets) 
bullock_corpus <- `docnames<-`(bullock_corpus, "bullock_2020primary")

swalwell2016primarytweets <- readLines("swalwelltweets.txt")
swalwell_corpus <- corpus(swalwell2016primarytweets) 
swalwell_corpus <- `docnames<-`(swalwell_corpus, "swalwell_2020primary")

#2016 & 2020 GENERAL ELECTION
  #2016
clinton2016_GE_tweets <- readLines("GE_hillary2016tweets.txt")
clinton2016_GE_corpus <- corpus(clinton2016_GE_tweets) 
clinton2016_GE_corpus <- `docnames<-`(clinton2016_GE_corpus, "clinton_2016_GE")

trump2016_GE_tweets <- readLines("GE2016_trumptweets.txt")
trump2016_GE_corpus <- corpus(trump2016_GE_tweets) 
trump2016_GE_corpus <- `docnames<-`(trump2016_GE_corpus, "trump_2016_GE")
  
  #2020
biden2020_GE_tweets <- readLines("GE_biden2020tweets.txt")
biden2020_GE_corpus <- corpus(biden2020_GE_tweets) 
biden2020_GE_corpus <- `docnames<-`(biden2020_GE_corpus, "biden_2020_GE")

trump2020_GE_tweets <- readLines("GE2020_trumptweets.txt")
trump2020_GE_corpus <- corpus(trump2020_GE_tweets) 
trump2020_GE_corpus <- `docnames<-`(trump2020_GE_corpus, "trump_2020_GE")
```


EXTRACT MORAL LANGAUGE 
Step 1: extract moral language from each 2016 REPUBLICAN candidate and write to a .txt file
```{r}
#Step 1: extract moral language from each candidate and write to a .txt file 

#TRUMP
#create tokens object from trump corpus 
toks_trump <- tokens(trump_corpus)

#select dictionary matches
moral_toks_trump <- tokens_select(toks_trump, pattern = data_dictionary_MFD, valuetype = "glob")

#convert to character string & concatenate :)
trump_moral <- as.character(moral_toks_trump)
trump_moral <- paste0(trump_moral, collapse = ". ")

#check how many dictionary matches, and then write to a .txt file
ntoken(trump_moral)
write(trump_moral, "trumpmoral.txt")

#CRUZ
toks_cruz <- tokens(cruz_corpus)
moral_toks_cruz <- tokens_select(toks_cruz, pattern = data_dictionary_MFD, valuetype = "glob")
cruz_moral <- as.character(moral_toks_cruz)
cruz_moral <- paste0(cruz_moral, collapse = ". ")
ntoken(cruz_moral)
write(cruz_moral, "cruzmoral.txt")

#RUBIO
toks_rubio <- tokens(rubio_corpus)
moral_toks_rubio <- tokens_select(toks_rubio, pattern = data_dictionary_MFD, valuetype = "glob")
rubio_moral <- as.character(moral_toks_rubio)
rubio_moral <- paste0(rubio_moral, collapse = ". ")
ntoken(rubio_moral)
write(rubio_moral, "rubiomoral.txt")

#KASICH
toks_kasich <- tokens(kasich_corpus)
moral_toks_kasich <- tokens_select(toks_kasich, pattern = data_dictionary_MFD, valuetype = "glob")
kasich_moral <- as.character(moral_toks_kasich)
kasich_moral <- paste0(kasich_moral, collapse = ". ")
ntoken(kasich_moral)
write(kasich_moral, "kasichmoral.txt")

#CARSON
toks_carson <- tokens(carson_corpus)
moral_toks_carson <- tokens_select(toks_carson, pattern = data_dictionary_MFD, valuetype = "glob")
carson_moral <- as.character(moral_toks_carson)
carson_moral <- paste0(carson_moral, collapse = ". ")
ntoken(carson_moral)
write(carson_moral, "carsonmoral.txt")

#BUSH
toks_bush <- tokens(bush_corpus)
moral_toks_bush <- tokens_select(toks_bush, pattern = data_dictionary_MFD, valuetype = "glob")
bush_moral <- as.character(moral_toks_bush)
bush_moral <- paste0(bush_moral, collapse = ". ")
ntoken(bush_moral)
write(bush_moral, "bushmoral.txt")

#CHRISTIE
toks_christie <- tokens(christie_corpus)
moral_toks_christie <- tokens_select(toks_christie, pattern = data_dictionary_MFD, valuetype = "glob")
christie_moral <- as.character(moral_toks_christie)
christie_moral <- paste0(christie_moral, collapse = ". ")
ntoken(christie_moral)
write(christie_moral, "christiemoral.txt")

#PAUL
toks_paul <- tokens(paul_corpus)
moral_toks_paul <- tokens_select(toks_paul, pattern = data_dictionary_MFD, valuetype = "glob")
paul_moral <- as.character(moral_toks_paul)
paul_moral <- paste0(paul_moral, collapse = ". ")
ntoken(paul_moral)
write(paul_moral, "paulmoral.txt")

#FIORINA
toks_fiorina <- tokens(fiorina_corpus)
moral_toks_fiorina <- tokens_select(toks_fiorina, pattern = data_dictionary_MFD, valuetype = "glob")
fiorina_moral <- as.character(moral_toks_fiorina)
fiorina_moral <- paste0(fiorina_moral, collapse = ". ")
ntoken(fiorina_moral)
write(fiorina_moral, "fiorinamoral.txt")

#HUCKABEE
toks_huckabee <- tokens(huckabee_corpus)
moral_toks_huckabee <- tokens_select(toks_huckabee, pattern = data_dictionary_MFD, valuetype = "glob")
huckabee_moral <- as.character(moral_toks_huckabee)
huckabee_moral <- paste0(huckabee_moral, collapse = ". ")
ntoken(huckabee_moral)
write(huckabee_moral, "huckabeemoral.txt")

#WALKER
toks_walker <- tokens(walker_corpus)
moral_toks_walker <- tokens_select(toks_walker, pattern = data_dictionary_MFD, valuetype = "glob")
walker_moral <- as.character(moral_toks_walker)
walker_moral <- paste0(walker_moral, collapse = ". ")
ntoken(walker_moral)
write(walker_moral, "walkermoral.txt")

#GRAHAM
toks_graham <- tokens(graham_corpus)
moral_toks_graham <- tokens_select(toks_graham, pattern = data_dictionary_MFD, valuetype = "glob")
graham_moral <- as.character(moral_toks_graham)
graham_moral <- paste0(graham_moral, collapse = ". ")
ntoken(graham_moral)
write(graham_moral, "grahammoral.txt")

#JINDAL
toks_jindal <- tokens(jindal_corpus)
moral_toks_jindal <- tokens_select(toks_jindal, pattern = data_dictionary_MFD, valuetype = "glob")
jindal_moral <- as.character(moral_toks_jindal)
jindal_moral <- paste0(jindal_moral, collapse = ". ")
ntoken(jindal_moral)
write(jindal_moral, "jindalmoral.txt")

#SANTORUM
toks_santorum <- tokens(santorum_corpus)
moral_toks_santorum <- tokens_select(toks_santorum, pattern = data_dictionary_MFD, valuetype = "glob")
santorum_moral <- as.character(moral_toks_santorum)
santorum_moral <- paste0(santorum_moral, collapse = ". ")
ntoken(santorum_moral)
write(santorum_moral, "santorummoral.txt")

#PATAKI
toks_pataki <- tokens(pataki_corpus)
moral_toks_pataki <- tokens_select(toks_pataki, pattern = data_dictionary_MFD, valuetype = "glob")
pataki_moral <- as.character(moral_toks_pataki)
pataki_moral <- paste0(pataki_moral, collapse = ". ")
ntoken(pataki_moral)
write(pataki_moral, "patakimoral.txt")

#PERRY
toks_perry <- tokens(perry_corpus)
moral_toks_perry <- tokens_select(toks_perry, pattern = data_dictionary_MFD, valuetype = "glob")
perry_moral <- as.character(moral_toks_perry)
perry_moral <- paste0(perry_moral, collapse = ". ")
ntoken(perry_moral)
write(perry_moral, "perrymoral.txt")
```
Step 2: extract moral language from each 2020 DEMOCRATIC candidate and write to a .txt file
```{r}
#BIDEN
toks_biden <- tokens(biden_corpus)
moral_toks_biden <- tokens_select(toks_biden, pattern = data_dictionary_MFD, valuetype = "glob")
biden_moral <- as.character(moral_toks_biden)
biden_moral <- paste0(biden_moral, collapse = ". ")
ntoken(biden_moral)
write(biden_moral, "bidenmoral.txt")

#SANDERS
toks_sanders <- tokens(sanders_corpus)
moral_toks_sanders <- tokens_select(toks_sanders, pattern = data_dictionary_MFD, valuetype = "glob")
sanders_moral <- as.character(moral_toks_sanders)
sanders_moral <- paste0(sanders_moral, collapse = ". ")
ntoken(sanders_moral)
write(sanders_moral, "sandersmoral.txt")

#BUTTIGIEG
toks_buttigieg <- tokens(buttigieg_corpus)
moral_toks_buttigieg <- tokens_select(toks_buttigieg, pattern = data_dictionary_MFD, valuetype = "glob")
buttigieg_moral <- as.character(moral_toks_buttigieg)
buttigieg_moral <- paste0(buttigieg_moral, collapse = ". ")
ntoken(buttigieg_moral)
write(buttigieg_moral, "buttigiegmoral.txt")

#WARREN
toks_warren <- tokens(warren_corpus)
moral_toks_warren <- tokens_select(toks_warren, pattern = data_dictionary_MFD, valuetype = "glob")
warren_moral <- as.character(moral_toks_warren)
warren_moral <- paste0(warren_moral, collapse = ". ")
ntoken(warren_moral)
write(warren_moral, "warrenmoral.txt")

#KLOBUCHAR
toks_klobuchar <- tokens(klobuchar_corpus)
moral_toks_klobuchar <- tokens_select(toks_klobuchar, pattern = data_dictionary_MFD, valuetype = "glob")
klobuchar_moral <- as.character(moral_toks_klobuchar)
klobuchar_moral <- paste0(klobuchar_moral, collapse = ". ")
ntoken(klobuchar_moral)
write(klobuchar_moral, "klobucharmoral.txt")

#HARRIS
toks_harris <- tokens(harris_corpus)
moral_toks_harris <- tokens_select(toks_harris, pattern = data_dictionary_MFD, valuetype = "glob")
harris_moral <- as.character(moral_toks_harris)
harris_moral <- paste0(harris_moral, collapse = ". ")
ntoken(harris_moral)
write(harris_moral, "harrismoral.txt")

#YANG
toks_yang <- tokens(yang_corpus)
moral_toks_yang <- tokens_select(toks_yang, pattern = data_dictionary_MFD, valuetype = "glob")
yang_moral <- as.character(moral_toks_yang)
yang_moral <- paste0(yang_moral, collapse = ". ")
ntoken(yang_moral)
write(yang_moral, "yangmoral.txt")

#STEYER
toks_steyer <- tokens(steyer_corpus)
moral_toks_steyer <- tokens_select(toks_steyer, pattern = data_dictionary_MFD, valuetype = "glob")
steyer_moral <- as.character(moral_toks_steyer)
steyer_moral <- paste0(steyer_moral, collapse = ". ")
ntoken(steyer_moral)
write(steyer_moral, "steyermoral.txt")

#BOOKER
toks_booker <- tokens(booker_corpus)
moral_toks_booker <- tokens_select(toks_booker, pattern = data_dictionary_MFD, valuetype = "glob")
booker_moral <- as.character(moral_toks_booker)
booker_moral <- paste0(booker_moral, collapse = ". ")
ntoken(booker_moral)
write(booker_moral, "bookermoral.txt")

#GABBARD
toks_gabbard <- tokens(gabbard_corpus)
moral_toks_gabbard <- tokens_select(toks_gabbard, pattern = data_dictionary_MFD, valuetype = "glob")
gabbard_moral <- as.character(moral_toks_gabbard)
gabbard_moral <- paste0(gabbard_moral, collapse = ". ")
ntoken(gabbard_moral)
write(gabbard_moral, "gabbardmoral.txt")

#CASTRO
toks_castro <- tokens(castro_corpus)
moral_toks_castro <- tokens_select(toks_castro, pattern = data_dictionary_MFD, valuetype = "glob")
castro_moral <- as.character(moral_toks_castro)
castro_moral <- paste0(castro_moral, collapse = ". ")
ntoken(castro_moral)
write(castro_moral, "castromoral.txt")

#O'ROURKE
toks_orourke <- tokens(orourke_corpus)
moral_toks_orourke <- tokens_select(toks_orourke, pattern = data_dictionary_MFD, valuetype = "glob")
orourke_moral <- as.character(moral_toks_orourke)
orourke_moral <- paste0(orourke_moral, collapse = ". ")
ntoken(orourke_moral)
write(orourke_moral, "orourkemoral.txt")

#BLOOMBERG
toks_bloomberg <- tokens(bloomberg_corpus)
moral_toks_bloomberg <- tokens_select(toks_bloomberg, pattern = data_dictionary_MFD, valuetype = "glob")
bloomberg_moral <- as.character(moral_toks_bloomberg)
bloomberg_moral <- paste0(bloomberg_moral, collapse = ". ")
ntoken(bloomberg_moral)
write(bloomberg_moral, "bloombergmoral.txt")

#BENNET
toks_bennet <- tokens(bennet_corpus)
moral_toks_bennet <- tokens_select(toks_bennet, pattern = data_dictionary_MFD, valuetype = "glob")
bennet_moral <- as.character(moral_toks_bennet)
bennet_moral <- paste0(bennet_moral, collapse = ". ")
ntoken(bennet_moral)
write(bennet_moral, "bennetmoral.txt")

#DELANEY
toks_delaney <- tokens(delaney_corpus)
moral_toks_delaney <- tokens_select(toks_delaney, pattern = data_dictionary_MFD, valuetype = "glob")
delaney_moral <- as.character(moral_toks_delaney)
delaney_moral <- paste0(delaney_moral, collapse = ". ")
ntoken(delaney_moral)
write(delaney_moral, "delaneymoral.txt")

#WILLIAMSON
toks_williamson <- tokens(williamson_corpus)
moral_toks_williamson <- tokens_select(toks_williamson, pattern = data_dictionary_MFD, valuetype = "glob")
williamson_moral <- as.character(moral_toks_williamson)
williamson_moral <- paste0(williamson_moral, collapse = ". ")
ntoken(williamson_moral)
write(williamson_moral, "williamsonmoral.txt")

#RYAN
toks_ryan <- tokens(ryan_corpus)
moral_toks_ryan <- tokens_select(toks_ryan, pattern = data_dictionary_MFD, valuetype = "glob")
ryan_moral <- as.character(moral_toks_ryan)
ryan_moral <- paste0(ryan_moral, collapse = ". ")
ntoken(ryan_moral)
write(ryan_moral, "ryanmoral.txt")

#DEBLASIO
toks_deblasio <- tokens(deblasio_corpus)
moral_toks_deblasio <- tokens_select(toks_deblasio, pattern = data_dictionary_MFD, valuetype = "glob")
deblasio_moral <- as.character(moral_toks_deblasio)
deblasio_moral <- paste0(deblasio_moral, collapse = ". ")
ntoken(deblasio_moral)
write(deblasio_moral, "deblasiomoral.txt")

#GILLIBRAND
toks_gillibrand <- tokens(gillibrand_corpus)
moral_toks_gillibrand <- tokens_select(toks_gillibrand, pattern = data_dictionary_MFD, valuetype = "glob")
gillibrand_moral <- as.character(moral_toks_gillibrand)
gillibrand_moral <- paste0(gillibrand_moral, collapse = ". ")
ntoken(gillibrand_moral)
write(gillibrand_moral, "gillibrandmoral.txt")

#INSLEE
toks_inslee <- tokens(inslee_corpus)
moral_toks_inslee <- tokens_select(toks_inslee, pattern = data_dictionary_MFD, valuetype = "glob")
inslee_moral <- as.character(moral_toks_inslee)
inslee_moral <- paste0(inslee_moral, collapse = ". ")
ntoken(inslee_moral)
write(inslee_moral, "insleemoral.txt")

#HICKENLOOPER
toks_hickenlooper <- tokens(hickenlooper_corpus)
moral_toks_hickenlooper <- tokens_select(toks_hickenlooper, pattern = data_dictionary_MFD, valuetype = "glob")
hickenlooper_moral <- as.character(moral_toks_hickenlooper)
hickenlooper_moral <- paste0(hickenlooper_moral, collapse = ". ")
ntoken(hickenlooper_moral)
write(hickenlooper_moral, "hickenloopermoral.txt")

#BULLOCK
toks_bullock <- tokens(bullock_corpus)
moral_toks_bullock <- tokens_select(toks_bullock, pattern = data_dictionary_MFD, valuetype = "glob")
bullock_moral <- as.character(moral_toks_bullock)
bullock_moral <- paste0(bullock_moral, collapse = ". ")
ntoken(bullock_moral)
write(bullock_moral, "bullockmoral.txt")

#SWALWELL
toks_swalwell <- tokens(swalwell_corpus)
moral_toks_swalwell <- tokens_select(toks_swalwell, pattern = data_dictionary_MFD, valuetype = "glob")
swalwell_moral <- as.character(moral_toks_swalwell)
swalwell_moral <- paste0(swalwell_moral, collapse = ". ")
ntoken(swalwell_moral)
write(swalwell_moral, "swalwellmoral.txt")
```
Step 3: extract moral language from each 2016 DEMOCRATIC candidate and write to a .txt file
```{r}
#CLINTON
toks_clinton_2016primary <- tokens(clinton2016primary_corpus)
toks_clinton_2016primary <- tokens_tolower(toks_clinton_2016primary)
moral_toks_clinton2016primary <- tokens_select(toks_clinton_2016primary, pattern = data_dictionary_MFD, valuetype = "glob")
clinton_moral2016primary <- as.character(moral_toks_clinton2016primary)
clinton_moral2016primary <- paste0(clinton_moral2016primary, collapse = ". ")
ntoken(clinton_moral2016primary)
write(clinton_moral2016primary, "clintonmoral2016primary.txt")


#SANDERS
toks_sanders_2016primary <- tokens(sanders2016primary_corpus)
toks_sanders_2016primary <- tokens_tolower(toks_sanders_2016primary)
moral_toks_sanders2016primary <- tokens_select(toks_sanders_2016primary, pattern = data_dictionary_MFD, valuetype = "glob")
sanders_moral2016primary <- as.character(moral_toks_sanders2016primary)
sanders_moral2016primary <- paste0(sanders_moral2016primary, collapse = ". ")
ntoken(sanders_moral2016primary)
write(sanders_moral2016primary, "sandersmoral2016primary.txt")

#O'MALLEY
toks_omalley_2016primary <- tokens(omalley2016primary_corpus)
toks_omalley_2016primary <- tokens_tolower(toks_omalley_2016primary)
moral_toks_omalley2016primary <- tokens_select(toks_omalley_2016primary, pattern = data_dictionary_MFD, valuetype = "glob")
omalley_moral2016primary <- as.character(moral_toks_omalley2016primary)
omalley_moral2016primary <- paste0(omalley_moral2016primary, collapse = ". ")
ntoken(omalley_moral2016primary)
write(omalley_moral2016primary, "omalleymoral2016primary.txt")
```
Step 4: extract moral language from 2016 & 2020 GE NOMINEES and write to a .txt file
```{r}
#CLINTON 2016
toks_clinton_2016GE <- tokens(clinton2016_GE_corpus)
moral_toks_clinton2016GE <- tokens_select(toks_clinton_2016GE, pattern = data_dictionary_MFD, valuetype = "glob")
clinton_moral2016GE <- as.character(moral_toks_clinton2016GE)
clinton_moral2016GE <- paste0(clinton_moral2016GE, collapse = ". ")
ntoken(clinton_moral2016GE)
write(clinton_moral2016GE, "clintonmoral2016GE.txt")

#TRUMP 2016
toks_trump_2016GE <- tokens(trump2016_GE_corpus)
moral_toks_trump2016GE <- tokens_select(toks_trump_2016GE, pattern = data_dictionary_MFD, valuetype = "glob")
trump_moral2016GE <- as.character(moral_toks_trump2016GE)
trump_moral2016GE <- paste0(trump_moral2016GE, collapse = ". ")
ntoken(trump_moral2016GE)
write(trump_moral2016GE, "trumpmoral2016GE.txt")

#BIDEN 2020
toks_biden_2020GE <- tokens(biden2020_GE_corpus)
moral_toks_biden2020GE <- tokens_select(toks_biden_2020GE, pattern = data_dictionary_MFD, valuetype = "glob")
biden_moral2020GE <- as.character(moral_toks_biden2020GE)
biden_moral2020GE <- paste0(biden_moral2020GE, collapse = ". ")
ntoken(biden_moral2020GE)
write(biden_moral2020GE, "bidenmoral2020GE.txt")

#TRUMP 2020 
toks_trump_2020GE <- tokens(trump2020_GE_corpus)
moral_toks_trump2020GE <- tokens_select(toks_trump_2020GE, pattern = data_dictionary_MFD, valuetype = "glob")
trump_moral2020GE <- as.character(moral_toks_trump2020GE)
trump_moral2020GE <- paste0(trump_moral2020GE, collapse = ". ")
ntoken(trump_moral2020GE)
write(trump_moral2020GE, "trumpmoral2020GE.txt")
```


DIVIDE INTO 5 MORAL FOUNDATIONS 
Step 5: calculate raw proportion of each moral foundation used by 2016 REPUBLICANS  
```{r}
#trump
trump_moral_dfm <- dfm(trump_moral, remove_punct=TRUE)
trump_moral_dfm <-dfm_weight(trump_moral_dfm, scheme = "prop")

dict_moral_trump <- dfm_lookup(trump_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_trump <- as.data.frame(dict_moral_trump)

data_moral_trump$care.virtue 
data_moral_trump$fairness.virtue 
data_moral_trump$loyalty.virtue 
data_moral_trump$authority.virtue 
data_moral_trump$sanctity.virtue 
data_moral_trump$care.vice 
data_moral_trump$fairness.vice 
data_moral_trump$loyalty.vice 
data_moral_trump$authority.vice 
data_moral_trump$sanctity.vice

#cruz
cruz_moral_dfm <- dfm(cruz_moral, remove_punct=TRUE)
cruz_moral_dfm <-dfm_weight(cruz_moral_dfm, scheme = "prop")

dict_moral_cruz <- dfm_lookup(cruz_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_cruz <- as.data.frame(dict_moral_cruz)

data_moral_cruz$care.virtue 
data_moral_cruz$fairness.virtue 
data_moral_cruz$loyalty.virtue 
data_moral_cruz$authority.virtue 
data_moral_cruz$sanctity.virtue 
data_moral_cruz$care.vice 
data_moral_cruz$fairness.vice 
data_moral_cruz$loyalty.vice 
data_moral_cruz$authority.vice 
data_moral_cruz$sanctity.vice 

#rubio
rubio_moral_dfm <- dfm(rubio_moral, remove_punct=TRUE)
rubio_moral_dfm <-dfm_weight(rubio_moral_dfm, scheme = "prop")

dict_moral_rubio <- dfm_lookup(rubio_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_rubio <- as.data.frame(dict_moral_rubio)

data_moral_rubio$care.virtue 
data_moral_rubio$fairness.virtue 
data_moral_rubio$loyalty.virtue 
data_moral_rubio$authority.virtue 
data_moral_rubio$sanctity.virtue 
data_moral_rubio$care.vice 
data_moral_rubio$fairness.vice 
data_moral_rubio$loyalty.vice 
data_moral_rubio$authority.vice 
data_moral_rubio$sanctity.vice 

#kasich
kasich_moral_dfm <- dfm(kasich_moral, remove_punct=TRUE)
kasich_moral_dfm <-dfm_weight(kasich_moral_dfm, scheme = "prop")

dict_moral_kasich <- dfm_lookup(kasich_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_kasich <- as.data.frame(dict_moral_kasich)

data_moral_kasich$care.virtue 
data_moral_kasich$fairness.virtue 
data_moral_kasich$loyalty.virtue 
data_moral_kasich$authority.virtue 
data_moral_kasich$sanctity.virtue 
data_moral_kasich$care.vice 
data_moral_kasich$fairness.vice 
data_moral_kasich$loyalty.vice 
data_moral_kasich$authority.vice 
data_moral_kasich$sanctity.vice 

#carson
carson_moral_dfm <- dfm(carson_moral, remove_punct=TRUE)
carson_moral_dfm <-dfm_weight(carson_moral_dfm, scheme = "prop")

dict_moral_carson <- dfm_lookup(carson_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_carson <- as.data.frame(dict_moral_carson)

data_moral_carson$care.virtue 
data_moral_carson$fairness.virtue 
data_moral_carson$loyalty.virtue 
data_moral_carson$authority.virtue 
data_moral_carson$sanctity.virtue 
data_moral_carson$care.vice 
data_moral_carson$fairness.vice 
data_moral_carson$loyalty.vice 
data_moral_carson$authority.vice 
data_moral_carson$sanctity.vice 

#bush
bush_moral_dfm <- dfm(bush_moral, remove_punct=TRUE)
bush_moral_dfm <-dfm_weight(bush_moral_dfm, scheme = "prop")

dict_moral_bush <- dfm_lookup(bush_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_bush <- as.data.frame(dict_moral_bush)

data_moral_bush$care.virtue 
data_moral_bush$fairness.virtue 
data_moral_bush$loyalty.virtue 
data_moral_bush$authority.virtue 
data_moral_bush$sanctity.virtue 
data_moral_bush$care.vice 
data_moral_bush$fairness.vice 
data_moral_bush$loyalty.vice 
data_moral_bush$authority.vice 
data_moral_bush$sanctity.vice 

#christie
christie_moral_dfm <- dfm(christie_moral, remove_punct=TRUE)
christie_moral_dfm <-dfm_weight(christie_moral_dfm, scheme = "prop")

dict_moral_christie <- dfm_lookup(christie_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_christie <- as.data.frame(dict_moral_christie)

data_moral_christie$care.virtue 
data_moral_christie$fairness.virtue 
data_moral_christie$loyalty.virtue 
data_moral_christie$authority.virtue 
data_moral_christie$sanctity.virtue 
data_moral_christie$care.vice 
data_moral_christie$fairness.vice 
data_moral_christie$loyalty.vice 
data_moral_christie$authority.vice 
data_moral_christie$sanctity.vice 

#paul
paul_moral_dfm <- dfm(paul_moral, remove_punct=TRUE)
paul_moral_dfm <-dfm_weight(paul_moral_dfm, scheme = "prop")

dict_moral_paul <- dfm_lookup(paul_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_paul <- as.data.frame(dict_moral_paul)

data_moral_paul$care.virtue 
data_moral_paul$fairness.virtue 
data_moral_paul$loyalty.virtue 
data_moral_paul$authority.virtue 
data_moral_paul$sanctity.virtue 
data_moral_paul$care.vice 
data_moral_paul$fairness.vice 
data_moral_paul$loyalty.vice 
data_moral_paul$authority.vice 
data_moral_paul$sanctity.vice 

#fiorina
fiorina_moral_dfm <- dfm(fiorina_moral, remove_punct=TRUE)
fiorina_moral_dfm <-dfm_weight(fiorina_moral_dfm, scheme = "prop")

dict_moral_fiorina <- dfm_lookup(fiorina_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_fiorina <- as.data.frame(dict_moral_fiorina)

data_moral_fiorina$care.virtue 
data_moral_fiorina$fairness.virtue 
data_moral_fiorina$loyalty.virtue 
data_moral_fiorina$authority.virtue 
data_moral_fiorina$sanctity.virtue 
data_moral_fiorina$care.vice 
data_moral_fiorina$fairness.vice 
data_moral_fiorina$loyalty.vice 
data_moral_fiorina$authority.vice 
data_moral_fiorina$sanctity.vice 

#huckabee
huckabee_moral_dfm <- dfm(huckabee_moral, remove_punct=TRUE)
huckabee_moral_dfm <-dfm_weight(huckabee_moral_dfm, scheme = "prop")

dict_moral_huckabee <- dfm_lookup(huckabee_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_huckabee <- as.data.frame(dict_moral_huckabee)

data_moral_huckabee$care.virtue 
data_moral_huckabee$fairness.virtue 
data_moral_huckabee$loyalty.virtue 
data_moral_huckabee$authority.virtue 
data_moral_huckabee$sanctity.virtue 
data_moral_huckabee$care.vice 
data_moral_huckabee$fairness.vice 
data_moral_huckabee$loyalty.vice 
data_moral_huckabee$authority.vice 
data_moral_huckabee$sanctity.vice 

#walker
walker_moral_dfm <- dfm(walker_moral, remove_punct=TRUE)
walker_moral_dfm <-dfm_weight(walker_moral_dfm, scheme = "prop")

dict_moral_walker <- dfm_lookup(walker_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_walker <- as.data.frame(dict_moral_walker)

data_moral_walker$care.virtue 
data_moral_walker$fairness.virtue 
data_moral_walker$loyalty.virtue 
data_moral_walker$authority.virtue 
data_moral_walker$sanctity.virtue 
data_moral_walker$care.vice 
data_moral_walker$fairness.vice 
data_moral_walker$loyalty.vice 
data_moral_walker$authority.vice 
data_moral_walker$sanctity.vice 

#graham
graham_moral_dfm <- dfm(graham_moral, remove_punct=TRUE)
graham_moral_dfm <-dfm_weight(graham_moral_dfm, scheme = "prop")

dict_moral_graham <- dfm_lookup(graham_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_graham <- as.data.frame(dict_moral_graham)

data_moral_graham$care.virtue 
data_moral_graham$fairness.virtue 
data_moral_graham$loyalty.virtue 
data_moral_graham$authority.virtue 
data_moral_graham$sanctity.virtue 
data_moral_graham$care.vice 
data_moral_graham$fairness.vice 
data_moral_graham$loyalty.vice 
data_moral_graham$authority.vice 
data_moral_graham$sanctity.vice 

#jindal
jindal_moral_dfm <- dfm(jindal_moral, remove_punct=TRUE)
jindal_moral_dfm <-dfm_weight(jindal_moral_dfm, scheme = "prop")

dict_moral_jindal <- dfm_lookup(jindal_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_jindal <- as.data.frame(dict_moral_jindal)

data_moral_jindal$care.virtue 
data_moral_jindal$fairness.virtue 
data_moral_jindal$loyalty.virtue 
data_moral_jindal$authority.virtue 
data_moral_jindal$sanctity.virtue 
data_moral_jindal$care.vice 
data_moral_jindal$fairness.vice 
data_moral_jindal$loyalty.vice 
data_moral_jindal$authority.vice 
data_moral_jindal$sanctity.vice 

#santorum
santorum_moral_dfm <- dfm(santorum_moral, remove_punct=TRUE)
santorum_moral_dfm <-dfm_weight(santorum_moral_dfm, scheme = "prop")

dict_moral_santorum <- dfm_lookup(santorum_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_santorum <- as.data.frame(dict_moral_santorum)

data_moral_santorum$care.virtue 
data_moral_santorum$fairness.virtue 
data_moral_santorum$loyalty.virtue 
data_moral_santorum$authority.virtue 
data_moral_santorum$sanctity.virtue 
data_moral_santorum$care.vice 
data_moral_santorum$fairness.vice 
data_moral_santorum$loyalty.vice 
data_moral_santorum$authority.vice 
data_moral_santorum$sanctity.vice 

#pataki
pataki_moral_dfm <- dfm(pataki_moral, remove_punct=TRUE)
pataki_moral_dfm <-dfm_weight(pataki_moral_dfm, scheme = "prop")

dict_moral_pataki <- dfm_lookup(pataki_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_pataki <- as.data.frame(dict_moral_pataki)

data_moral_pataki$care.virtue 
data_moral_pataki$fairness.virtue 
data_moral_pataki$loyalty.virtue 
data_moral_pataki$authority.virtue 
data_moral_pataki$sanctity.virtue 
data_moral_pataki$care.vice 
data_moral_pataki$fairness.vice 
data_moral_pataki$loyalty.vice 
data_moral_pataki$authority.vice 
data_moral_pataki$sanctity.vice 

#perry
perry_moral_dfm <- dfm(perry_moral, remove_punct=TRUE)
perry_moral_dfm <-dfm_weight(perry_moral_dfm, scheme = "prop")

dict_moral_perry <- dfm_lookup(perry_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_perry <- as.data.frame(dict_moral_perry)

data_moral_perry$care.virtue 
data_moral_perry$fairness.virtue 
data_moral_perry$loyalty.virtue 
data_moral_perry$authority.virtue 
data_moral_perry$sanctity.virtue 
data_moral_perry$care.vice 
data_moral_perry$fairness.vice 
data_moral_perry$loyalty.vice 
data_moral_perry$authority.vice 
data_moral_perry$sanctity.vice 
```
Step 6: calculate raw proportion of each moral foundation used by 2020 DEMOCRATS
```{r}
#BIDEN
biden_moral_dfm <- dfm(biden_moral, remove_punct=TRUE)
biden_moral_dfm <-dfm_weight(biden_moral_dfm, scheme = "prop")

dict_moral_biden <- dfm_lookup(biden_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_biden <- as.data.frame(dict_moral_biden)

data_moral_biden$care.virtue 
data_moral_biden$fairness.virtue 
data_moral_biden$loyalty.virtue 
data_moral_biden$authority.virtue 
data_moral_biden$sanctity.virtue 
data_moral_biden$care.vice 
data_moral_biden$fairness.vice 
data_moral_biden$loyalty.vice 
data_moral_biden$authority.vice 
data_moral_biden$sanctity.vice 

#SANDERS
sanders_moral_dfm <- dfm(sanders_moral, remove_punct=TRUE)
sanders_moral_dfm <-dfm_weight(sanders_moral_dfm, scheme = "prop")

dict_moral_sanders <- dfm_lookup(sanders_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_sanders <- as.data.frame(dict_moral_sanders)

data_moral_sanders$care.virtue # 0.2951413
data_moral_sanders$fairness.virtue # 0.08349261
data_moral_sanders$loyalty.virtue # 0.257117
data_moral_sanders$authority.virtue # 0.1289609
data_moral_sanders$sanctity.virtue # 0.02846796
data_moral_sanders$care.vice # 0.1222211
data_moral_sanders$fairness.vice #  0.03480535
data_moral_sanders$loyalty.vice # 0.003218992
data_moral_sanders$authority.vice # 0.008449854 
data_moral_sanders$sanctity.vice # 0.05230862

#WARREN
warren_moral_dfm <- dfm(warren_moral, remove_punct=TRUE)
warren_moral_dfm <-dfm_weight(warren_moral_dfm, scheme = "prop")

dict_moral_warren <- dfm_lookup(warren_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_warren <- as.data.frame(dict_moral_warren)

data_moral_warren$care.virtue # 0.2144479
data_moral_warren$fairness.virtue # 0.08820089
data_moral_warren$loyalty.virtue # 0.2282078
data_moral_warren$authority.virtue # 0.1375301
data_moral_warren$sanctity.virtue # 0.02187822
data_moral_warren$care.vice # 0.2272446
data_moral_warren$fairness.vice # 0.0372893
data_moral_warren$loyalty.vice #   0.0003439972
data_moral_warren$authority.vice #  0.005985552
data_moral_warren$sanctity.vice # 0.05304438

#KLOBUCHAR
klobuchar_moral_dfm <- dfm(klobuchar_moral, remove_punct=TRUE)
klobuchar_moral_dfm <-dfm_weight(klobuchar_moral_dfm, scheme = "prop")

dict_moral_klobuchar <- dfm_lookup(klobuchar_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_klobuchar <- as.data.frame(dict_moral_klobuchar)

data_moral_klobuchar$care.virtue # 0.2263856
data_moral_klobuchar$fairness.virtue # 0.08665105
data_moral_klobuchar$loyalty.virtue # 0.2466823
data_moral_klobuchar$authority.virtue # 0.2534478
data_moral_klobuchar$sanctity.virtue # 0.03148582
data_moral_klobuchar$care.vice # 0.1074681
data_moral_klobuchar$fairness.vice # 0.0156128
data_moral_klobuchar$loyalty.vice #   0.00156128
data_moral_klobuchar$authority.vice #  0.007285974
data_moral_klobuchar$sanctity.vice # 0.04553734

#BUTTIGIEG
buttigieg_moral_dfm <- dfm(buttigieg_moral, remove_punct=TRUE)
buttigieg_moral_dfm <-dfm_weight(buttigieg_moral_dfm, scheme = "prop")

dict_moral_buttigieg <- dfm_lookup(buttigieg_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_buttigieg <- as.data.frame(dict_moral_buttigieg)

data_moral_buttigieg$care.virtue # 0.2348873
data_moral_buttigieg$fairness.virtue # 0.08606557
data_moral_buttigieg$loyalty.virtue # 0.3007172
data_moral_buttigieg$authority.virtue # 0.2005635
data_moral_buttigieg$sanctity.virtue # 0.03714139
data_moral_buttigieg$care.vice # 0.08760246
data_moral_buttigieg$fairness.vice # 0.03150615
data_moral_buttigieg$loyalty.vice #   0.00204918
data_moral_buttigieg$authority.vice #  0.006915984
data_moral_buttigieg$sanctity.vice # 0.01895492

#YANG
yang_moral_dfm <- dfm(yang_moral, remove_punct=TRUE)
yang_moral_dfm <-dfm_weight(yang_moral_dfm, scheme = "prop")

dict_moral_yang <- dfm_lookup(yang_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_yang <- as.data.frame(dict_moral_yang)

data_moral_yang$care.virtue # 0.2742857
data_moral_yang$fairness.virtue # 0.04707483
data_moral_yang$loyalty.virtue # 0.2778231
data_moral_yang$authority.virtue # 0.2234014
data_moral_yang$sanctity.virtue # 0.04680272
data_moral_yang$care.vice # 0.07183673
data_moral_yang$fairness.vice # 0.01605442
data_moral_yang$loyalty.vice #   0.002993197
data_moral_yang$authority.vice #  0.001632653
data_moral_yang$sanctity.vice # 0.04435374

#STEYER
steyer_moral_dfm <- dfm(steyer_moral, remove_punct=TRUE)
steyer_moral_dfm <-dfm_weight(steyer_moral_dfm, scheme = "prop")

dict_moral_steyer <- dfm_lookup(steyer_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_steyer <- as.data.frame(dict_moral_steyer)

data_moral_steyer$care.virtue # 0.2558654
data_moral_steyer$fairness.virtue # 0.0894201
data_moral_steyer$loyalty.virtue # 0.1646746
data_moral_steyer$authority.virtue # 0.2246569
data_moral_steyer$sanctity.virtue # 0.02567508
data_moral_steyer$care.vice # 0.1164232
data_moral_steyer$fairness.vice # 0.09871625
data_moral_steyer$loyalty.vice #   0.005754759
data_moral_steyer$authority.vice #  0.008410801
data_moral_steyer$sanctity.vice # 0.03098716

#HARRIS
harris_moral_dfm <- dfm(harris_moral, remove_punct=TRUE)
harris_moral_dfm <-dfm_weight(harris_moral_dfm, scheme = "prop")

dict_moral_harris <- dfm_lookup(harris_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_harris <- as.data.frame(dict_moral_harris)

data_moral_harris$care.virtue # 0.2292484
data_moral_harris$fairness.virtue # 0.1139701
data_moral_harris$loyalty.virtue # 0.2025004
data_moral_harris$authority.virtue # 0.1955226
data_moral_harris$sanctity.virtue # 0.03445268
data_moral_harris$care.vice # 0.1804041
data_moral_harris$fairness.vice # 0.02936473
data_moral_harris$loyalty.vice #   0.0014537
data_moral_harris$authority.vice #  0.006105539
data_moral_harris$sanctity.vice # 0.02500363

#BOOKER
booker_moral_dfm <- dfm(booker_moral, remove_punct=TRUE)
booker_moral_dfm <-dfm_weight(booker_moral_dfm, scheme = "prop")

dict_moral_booker <- dfm_lookup(booker_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_booker <- as.data.frame(dict_moral_booker)

data_moral_booker$care.virtue #  0.2180451
data_moral_booker$fairness.virtue # 0.1163202
data_moral_booker$loyalty.virtue # 0.2494471
data_moral_booker$authority.virtue # 0.1508182
data_moral_booker$sanctity.virtue # 0.0495356
data_moral_booker$care.vice # 0.1510394
data_moral_booker$fairness.vice # 0.03162318
data_moral_booker$loyalty.vice #   0.0008845644
data_moral_booker$authority.vice #  0.005307386
data_moral_booker$sanctity.vice # 0.036046

#GABBARD
gabbard_moral_dfm <- dfm(gabbard_moral, remove_punct=TRUE)
gabbard_moral_dfm <-dfm_weight(gabbard_moral_dfm, scheme = "prop")

dict_moral_gabbard <- dfm_lookup(gabbard_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_gabbard <- as.data.frame(dict_moral_gabbard)

data_moral_gabbard$care.virtue 
data_moral_gabbard$fairness.virtue 
data_moral_gabbard$loyalty.virtue 
data_moral_gabbard$authority.virtue 
data_moral_gabbard$sanctity.virtue 
data_moral_gabbard$care.vice 
data_moral_gabbard$fairness.vice 
data_moral_gabbard$loyalty.vice 
data_moral_gabbard$authority.vice 
data_moral_gabbard$sanctity.vice 

#CASTRO
castro_moral_dfm <- dfm(castro_moral, remove_punct=TRUE)
castro_moral_dfm <-dfm_weight(castro_moral_dfm, scheme = "prop")

dict_moral_castro <- dfm_lookup(castro_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_castro <- as.data.frame(dict_moral_castro)

data_moral_castro$care.virtue 
data_moral_castro$fairness.virtue 
data_moral_castro$loyalty.virtue 
data_moral_castro$authority.virtue 
data_moral_castro$sanctity.virtue 
data_moral_castro$care.vice 
data_moral_castro$fairness.vice 
data_moral_castro$loyalty.vice 
data_moral_castro$authority.vice 
data_moral_castro$sanctity.vice 

#OROURKE
orourke_moral_dfm <- dfm(orourke_moral, remove_punct=TRUE)
orourke_moral_dfm <-dfm_weight(orourke_moral_dfm, scheme = "prop")

dict_moral_orourke <- dfm_lookup(orourke_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_orourke <- as.data.frame(dict_moral_orourke)

data_moral_orourke$care.virtue 
data_moral_orourke$fairness.virtue 
data_moral_orourke$loyalty.virtue 
data_moral_orourke$authority.virtue 
data_moral_orourke$sanctity.virtue 
data_moral_orourke$care.vice 
data_moral_orourke$fairness.vice 
data_moral_orourke$loyalty.vice 
data_moral_orourke$authority.vice 
data_moral_orourke$sanctity.vice 

#BLOOMBERG
bloomberg_moral_dfm <- dfm(bloomberg_moral, remove_punct=TRUE)
bloomberg_moral_dfm <-dfm_weight(bloomberg_moral_dfm, scheme = "prop")

dict_moral_bloomberg <- dfm_lookup(bloomberg_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_bloomberg <- as.data.frame(dict_moral_bloomberg)

data_moral_bloomberg$care.virtue 
data_moral_bloomberg$fairness.virtue 
data_moral_bloomberg$loyalty.virtue 
data_moral_bloomberg$authority.virtue 
data_moral_bloomberg$sanctity.virtue 
data_moral_bloomberg$care.vice 
data_moral_bloomberg$fairness.vice 
data_moral_bloomberg$loyalty.vice 
data_moral_bloomberg$authority.vice 
data_moral_bloomberg$sanctity.vice 

#BENNET
bennet_moral_dfm <- dfm(bennet_moral, remove_punct=TRUE)
bennet_moral_dfm <-dfm_weight(bennet_moral_dfm, scheme = "prop")

dict_moral_bennet <- dfm_lookup(bennet_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_bennet <- as.data.frame(dict_moral_bennet)

data_moral_bennet$care.virtue 
data_moral_bennet$fairness.virtue 
data_moral_bennet$loyalty.virtue 
data_moral_bennet$authority.virtue 
data_moral_bennet$sanctity.virtue 
data_moral_bennet$care.vice 
data_moral_bennet$fairness.vice 
data_moral_bennet$loyalty.vice 
data_moral_bennet$authority.vice 
data_moral_bennet$sanctity.vice 

#DELANEY
delaney_moral_dfm <- dfm(delaney_moral, remove_punct=TRUE)
delaney_moral_dfm <-dfm_weight(delaney_moral_dfm, scheme = "prop")

dict_moral_delaney <- dfm_lookup(delaney_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_delaney <- as.data.frame(dict_moral_delaney)

data_moral_delaney$care.virtue 
data_moral_delaney$fairness.virtue 
data_moral_delaney$loyalty.virtue 
data_moral_delaney$authority.virtue 
data_moral_delaney$sanctity.virtue 
data_moral_delaney$care.vice 
data_moral_delaney$fairness.vice 
data_moral_delaney$loyalty.vice 
data_moral_delaney$authority.vice 
data_moral_delaney$sanctity.vice 

#WILLIAMSON
williamson_moral_dfm <- dfm(williamson_moral, remove_punct=TRUE)
williamson_moral_dfm <-dfm_weight(williamson_moral_dfm, scheme = "prop")

dict_moral_williamson <- dfm_lookup(williamson_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_williamson <- as.data.frame(dict_moral_williamson)

data_moral_williamson$care.virtue 
data_moral_williamson$fairness.virtue 
data_moral_williamson$loyalty.virtue 
data_moral_williamson$authority.virtue 
data_moral_williamson$sanctity.virtue 
data_moral_williamson$care.vice 
data_moral_williamson$fairness.vice 
data_moral_williamson$loyalty.vice 
data_moral_williamson$authority.vice 
data_moral_williamson$sanctity.vice 

#RYAN
ryan_moral_dfm <- dfm(ryan_moral, remove_punct=TRUE)
ryan_moral_dfm <-dfm_weight(ryan_moral_dfm, scheme = "prop")

dict_moral_ryan <- dfm_lookup(ryan_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_ryan <- as.data.frame(dict_moral_ryan)

data_moral_ryan$care.virtue 
data_moral_ryan$fairness.virtue 
data_moral_ryan$loyalty.virtue 
data_moral_ryan$authority.virtue 
data_moral_ryan$sanctity.virtue 
data_moral_ryan$care.vice 
data_moral_ryan$fairness.vice 
data_moral_ryan$loyalty.vice 
data_moral_ryan$authority.vice 
data_moral_ryan$sanctity.vice 

#DE BLASIO
deblasio_moral_dfm <- dfm(deblasio_moral, remove_punct=TRUE)
deblasio_moral_dfm <-dfm_weight(deblasio_moral_dfm, scheme = "prop")

dict_moral_deblasio <- dfm_lookup(deblasio_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_deblasio <- as.data.frame(dict_moral_deblasio)

data_moral_deblasio$care.virtue 
data_moral_deblasio$fairness.virtue 
data_moral_deblasio$loyalty.virtue 
data_moral_deblasio$authority.virtue 
data_moral_deblasio$sanctity.virtue 
data_moral_deblasio$care.vice 
data_moral_deblasio$fairness.vice 
data_moral_deblasio$loyalty.vice 
data_moral_deblasio$authority.vice 
data_moral_deblasio$sanctity.vice 

#GILLIBRAND
gillibrand_moral_dfm <- dfm(gillibrand_moral, remove_punct=TRUE)
gillibrand_moral_dfm <-dfm_weight(gillibrand_moral_dfm, scheme = "prop")

dict_moral_gillibrand <- dfm_lookup(gillibrand_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_gillibrand <- as.data.frame(dict_moral_gillibrand)

data_moral_gillibrand$care.virtue 
data_moral_gillibrand$fairness.virtue 
data_moral_gillibrand$loyalty.virtue 
data_moral_gillibrand$authority.virtue 
data_moral_gillibrand$sanctity.virtue 
data_moral_gillibrand$care.vice 
data_moral_gillibrand$fairness.vice 
data_moral_gillibrand$loyalty.vice 
data_moral_gillibrand$authority.vice 
data_moral_gillibrand$sanctity.vice 

#INSLEE
inslee_moral_dfm <- dfm(inslee_moral, remove_punct=TRUE)
inslee_moral_dfm <-dfm_weight(inslee_moral_dfm, scheme = "prop")

dict_moral_inslee <- dfm_lookup(inslee_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_inslee <- as.data.frame(dict_moral_inslee)

data_moral_inslee$care.virtue 
data_moral_inslee$fairness.virtue 
data_moral_inslee$loyalty.virtue 
data_moral_inslee$authority.virtue 
data_moral_inslee$sanctity.virtue 
data_moral_inslee$care.vice 
data_moral_inslee$fairness.vice 
data_moral_inslee$loyalty.vice 
data_moral_inslee$authority.vice 
data_moral_inslee$sanctity.vice 

#HICKENLOOPER
hickenlooper_moral_dfm <- dfm(hickenlooper_moral, remove_punct=TRUE)
hickenlooper_moral_dfm <-dfm_weight(hickenlooper_moral_dfm, scheme = "prop")

dict_moral_hickenlooper <- dfm_lookup(hickenlooper_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_hickenlooper <- as.data.frame(dict_moral_hickenlooper)

data_moral_hickenlooper$care.virtue 
data_moral_hickenlooper$fairness.virtue 
data_moral_hickenlooper$loyalty.virtue 
data_moral_hickenlooper$authority.virtue 
data_moral_hickenlooper$sanctity.virtue 
data_moral_hickenlooper$care.vice 
data_moral_hickenlooper$fairness.vice 
data_moral_hickenlooper$loyalty.vice 
data_moral_hickenlooper$authority.vice 
data_moral_hickenlooper$sanctity.vice 

#BULLOCK
bullock_moral_dfm <- dfm(bullock_moral, remove_punct=TRUE)
bullock_moral_dfm <-dfm_weight(bullock_moral_dfm, scheme = "prop")

dict_moral_bullock <- dfm_lookup(bullock_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_bullock <- as.data.frame(dict_moral_bullock)

data_moral_bullock$care.virtue 
data_moral_bullock$fairness.virtue 
data_moral_bullock$loyalty.virtue 
data_moral_bullock$authority.virtue 
data_moral_bullock$sanctity.virtue 
data_moral_bullock$care.vice 
data_moral_bullock$fairness.vice 
data_moral_bullock$loyalty.vice 
data_moral_bullock$authority.vice 
data_moral_bullock$sanctity.vice 

#SWALWELL
swalwell_moral_dfm <- dfm(swalwell_moral, remove_punct=TRUE)
swalwell_moral_dfm <-dfm_weight(swalwell_moral_dfm, scheme = "prop")

dict_moral_swalwell <- dfm_lookup(swalwell_moral_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_swalwell <- as.data.frame(dict_moral_swalwell)

data_moral_swalwell$care.virtue 
data_moral_swalwell$fairness.virtue 
data_moral_swalwell$loyalty.virtue 
data_moral_swalwell$authority.virtue 
data_moral_swalwell$sanctity.virtue 
data_moral_swalwell$care.vice 
data_moral_swalwell$fairness.vice 
data_moral_swalwell$loyalty.vice 
data_moral_swalwell$authority.vice 
data_moral_swalwell$sanctity.vice 
```
Step 7: calculate raw proportion of each moral foundation used by 2016 DEMOCRATS
```{r}
#CLINTON
clinton_moral2016primary_dfm <- dfm(clinton_moral2016primary, remove_punct=TRUE)
clinton_moral2016primary_dfm <-dfm_weight(clinton_moral2016primary_dfm, scheme = "prop")
sum(ntoken(clinton_moral2016primary))
dict_moral_clinton2016primary <- dfm_lookup(clinton_moral2016primary_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_clinton2016primary <- as.data.frame(dict_moral_clinton2016primary)

data_moral_clinton2016primary$care.virtue 
data_moral_clinton2016primary$fairness.virtue 
data_moral_clinton2016primary$loyalty.virtue 
data_moral_clinton2016primary$authority.virtue 
data_moral_clinton2016primary$sanctity.virtue 
data_moral_clinton2016primary$care.vice 
data_moral_clinton2016primary$fairness.vice 
data_moral_clinton2016primary$loyalty.vice 
data_moral_clinton2016primary$authority.vice 
data_moral_clinton2016primary$sanctity.vice 

#SANDERS
sanders_moral2016primary_dfm <- dfm(sanders_moral2016primary, remove_punct=TRUE)
sanders_moral2016primary_dfm <-dfm_weight(sanders_moral2016primary_dfm, scheme = "prop")

dict_moral_sanders2016primary <- dfm_lookup(sanders_moral2016primary_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_sanders2016primary <- as.data.frame(dict_moral_sanders2016primary)

data_moral_sanders2016primary$care.virtue 
data_moral_sanders2016primary$fairness.virtue 
data_moral_sanders2016primary$loyalty.virtue 
data_moral_sanders2016primary$authority.virtue 
data_moral_sanders2016primary$sanctity.virtue 
data_moral_sanders2016primary$care.vice 
data_moral_sanders2016primary$fairness.vice 
data_moral_sanders2016primary$loyalty.vice 
data_moral_sanders2016primary$authority.vice 
data_moral_sanders2016primary$sanctity.vice  

#OMALLEY
omalley_moral2016primary_dfm <- dfm(omalley_moral2016primary, remove_punct=TRUE)
omalley_moral2016primary_dfm <-dfm_weight(omalley_moral2016primary_dfm, scheme = "prop")

dict_moral_omalley2016primary <- dfm_lookup(omalley_moral2016primary_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_omalley2016primary <- as.data.frame(dict_moral_omalley2016primary)

data_moral_omalley2016primary$care.virtue 
data_moral_omalley2016primary$fairness.virtue 
data_moral_omalley2016primary$loyalty.virtue 
data_moral_omalley2016primary$authority.virtue 
data_moral_omalley2016primary$sanctity.virtue 
data_moral_omalley2016primary$care.vice 
data_moral_omalley2016primary$fairness.vice 
data_moral_omalley2016primary$loyalty.vice 
data_moral_omalley2016primary$authority.vice 
data_moral_omalley2016primary$sanctity.vice 
```
Step 8: calculate raw proportion from 2016 & 2020 GE NOMINEES
```{r}
#CLINTON 2016
clinton_moral2016_GE_dfm <- dfm(clinton_moral2016GE, remove_punct=TRUE)
clinton_moral2016_GE_dfm <-dfm_weight(clinton_moral2016_GE_dfm, scheme = "prop")

dict_moral_clinton2016_GE <- dfm_lookup(clinton_moral2016_GE_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_clinton2016_GE <- as.data.frame(dict_moral_clinton2016_GE)

data_moral_clinton2016_GE$care.virtue 
data_moral_clinton2016_GE$fairness.virtue 
data_moral_clinton2016_GE$loyalty.virtue 
data_moral_clinton2016_GE$authority.virtue 
data_moral_clinton2016_GE$sanctity.virtue 
data_moral_clinton2016_GE$care.vice 
data_moral_clinton2016_GE$fairness.vice 
data_moral_clinton2016_GE$loyalty.vice 
data_moral_clinton2016_GE$authority.vice 
data_moral_clinton2016_GE$sanctity.vice 

#TRUMP 2016
trump_moral2016_GE_dfm <- dfm(trump_moral2016GE, remove_punct=TRUE, remove = "crooked")
trump_moral2016_GE_dfm <-dfm_weight(trump_moral2016_GE_dfm, scheme = "prop")

dict_moral_trump2016_GE <- dfm_lookup(trump_moral2016_GE_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_trump2016_GE <- as.data.frame(dict_moral_trump2016_GE)

data_moral_trump2016_GE$care.virtue 
data_moral_trump2016_GE$fairness.virtue 
data_moral_trump2016_GE$loyalty.virtue 
data_moral_trump2016_GE$authority.virtue 
data_moral_trump2016_GE$sanctity.virtue 
data_moral_trump2016_GE$care.vice 
data_moral_trump2016_GE$fairness.vice 
data_moral_trump2016_GE$loyalty.vice 
data_moral_trump2016_GE$authority.vice 
data_moral_trump2016_GE$sanctity.vice

#BIDEN 2020
biden_moral2020_GE_dfm <- dfm(biden_moral2020GE, remove_punct=TRUE)
biden_moral2020_GE_dfm <-dfm_weight(biden_moral2020_GE_dfm, scheme = "prop")

dict_moral_biden2020_GE <- dfm_lookup(biden_moral2020_GE_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_biden2020_GE <- as.data.frame(dict_moral_biden2020_GE)

data_moral_biden2020_GE$care.virtue 
data_moral_biden2020_GE$fairness.virtue 
data_moral_biden2020_GE$loyalty.virtue 
data_moral_biden2020_GE$authority.virtue 
data_moral_biden2020_GE$sanctity.virtue 
data_moral_biden2020_GE$care.vice 
data_moral_biden2020_GE$fairness.vice 
data_moral_biden2020_GE$loyalty.vice 
data_moral_biden2020_GE$authority.vice 
data_moral_biden2020_GE$sanctity.vice 

#TRUMP 2020
trump_moral2020_GE_dfm <- dfm(trump_moral2020GE, remove_punct=TRUE)
trump_moral2020_GE_dfm <-dfm_weight(trump_moral2020_GE_dfm, scheme = "prop")

dict_moral_trump2020_GE <- dfm_lookup(trump_moral2020_GE_dfm, dictionary = data_dictionary_MFD, verbose = FALSE)
data_moral_trump2020_GE <- as.data.frame(dict_moral_trump2020_GE)

data_moral_trump2020_GE$care.virtue 
data_moral_trump2020_GE$fairness.virtue 
data_moral_trump2020_GE$loyalty.virtue 
data_moral_trump2020_GE$authority.virtue 
data_moral_trump2020_GE$sanctity.virtue 
data_moral_trump2020_GE$care.vice 
data_moral_trump2020_GE$fairness.vice 
data_moral_trump2020_GE$loyalty.vice 
data_moral_trump2020_GE$authority.vice 
data_moral_trump2020_GE$sanctity.vice

trump_fairness.vice <- tokens_select(toks_trump_2016GE, pattern = data_dictionary_MFD$fairness.vice, valuetype = "glob")
trump_fairness.vice <- as.character(trump_fairness.vice) #crooked :/
```


WEIGHT & FILTER 
Step 9: Unweight dfm's and add document names & add min_term_freq of 3 to help compute more accurate tf-idf later
```{r}
#unweight and add document names, add min_term freq of 2 to help compute more accurate tf-idf later
  #repubs 2016
trump_moral_dfm <- dfm(trump_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
trump_moral_dfm <- dfm_trim(trump_moral_dfm, min_termfreq = 3)
trump_moral_dfm <- `docnames<-`(trump_moral_dfm, "trump_moral_dfm")
cruz_moral_dfm <- dfm(cruz_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
cruz_moral_dfm <- dfm_trim(cruz_moral_dfm, min_termfreq = 3)
cruz_moral_dfm <- `docnames<-`(cruz_moral_dfm, "cruz_moral_dfm")
rubio_moral_dfm <- dfm(rubio_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
rubio_moral_dfm <- dfm_trim(rubio_moral_dfm, min_termfreq = 3)
rubio_moral_dfm <- `docnames<-`(rubio_moral_dfm, "rubio_moral_dfm")
kasich_moral_dfm <- dfm(kasich_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
kasich_moral_dfm <- dfm_trim(kasich_moral_dfm, min_termfreq = 3)
kasich_moral_dfm <- `docnames<-`(kasich_moral_dfm, "kasich_moral_dfm")
carson_moral_dfm <- dfm(carson_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
carson_moral_dfm <- dfm_trim(carson_moral_dfm, min_termfreq = 3)
carson_moral_dfm <- `docnames<-`(carson_moral_dfm, "carson_moral_dfm")
bush_moral_dfm <- dfm(bush_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
bush_moral_dfm <- dfm_trim(bush_moral_dfm, min_termfreq = 3)
bush_moral_dfm <- `docnames<-`(bush_moral_dfm, "bush_moral_dfm")
christie_moral_dfm <- dfm(christie_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
christie_moral_dfm <- dfm_trim(christie_moral_dfm, min_termfreq = 3)
christie_moral_dfm <- `docnames<-`(christie_moral_dfm, "christie_moral_dfm")
paul_moral_dfm <- dfm(paul_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
paul_moral_dfm <- dfm_trim(paul_moral_dfm, min_termfreq = 3)
paul_moral_dfm <- `docnames<-`(paul_moral_dfm, "paul_moral_dfm")
fiorina_moral_dfm <- dfm(fiorina_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
fiorina_moral_dfm <- dfm_trim(fiorina_moral_dfm, min_termfreq = 3)
fiorina_moral_dfm <- `docnames<-`(fiorina_moral_dfm, "fiorina_moral_dfm")
huckabee_moral_dfm <- dfm(huckabee_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
huckabee_moral_dfm <- dfm_trim(huckabee_moral_dfm, min_termfreq = 3)
huckabee_moral_dfm <- `docnames<-`(huckabee_moral_dfm, "huckabee_moral_dfm")
walker_moral_dfm <- dfm(walker_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
walker_moral_dfm <- dfm_trim(walker_moral_dfm, min_termfreq = 3)
walker_moral_dfm <- `docnames<-`(walker_moral_dfm, "walker_moral_dfm")
graham_moral_dfm <- dfm(graham_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
graham_moral_dfm <- dfm_trim(graham_moral_dfm, min_termfreq = 3)
graham_moral_dfm <- `docnames<-`(graham_moral_dfm, "graham_moral_dfm")
jindal_moral_dfm <- dfm(jindal_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
jindal_moral_dfm <- dfm_trim(jindal_moral_dfm, min_termfreq = 3)
jindal_moral_dfm <- `docnames<-`(jindal_moral_dfm, "jindal_moral_dfm")
santorum_moral_dfm <- dfm(santorum_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
santorum_moral_dfm <- dfm_trim(santorum_moral_dfm, min_termfreq = 3)
santorum_moral_dfm <- `docnames<-`(santorum_moral_dfm, "santorum_moral_dfm")
pataki_moral_dfm <- dfm(pataki_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
pataki_moral_dfm <- dfm_trim(pataki_moral_dfm, min_termfreq = 3)
pataki_moral_dfm <- `docnames<-`(pataki_moral_dfm, "pataki_moral_dfm")
perry_moral_dfm <- dfm(perry_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
perry_moral_dfm <- dfm_trim(perry_moral_dfm, min_termfreq = 3)
perry_moral_dfm <- `docnames<-`(perry_moral_dfm, "perry_moral_dfm")

  #dems 2020
biden_moral_dfm <- dfm(biden_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
biden_moral_dfm <- dfm_trim(biden_moral_dfm, min_termfreq = 3)
biden_moral_dfm <- `docnames<-`(biden_moral_dfm, "biden_moral_dfm")
sanders_moral_dfm <- dfm(sanders_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
sanders_moral_dfm <- dfm_trim(sanders_moral_dfm, min_termfreq = 3)
sanders_moral_dfm <- `docnames<-`(sanders_moral_dfm, "sanders_moral_dfm")
warren_moral_dfm <- dfm(warren_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
warren_moral_dfm <- dfm_trim(warren_moral_dfm, min_termfreq = 3)
warren_moral_dfm <- `docnames<-`(warren_moral_dfm, "warren_moral_dfm")
buttigieg_moral_dfm <- dfm(buttigieg_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
buttigieg_moral_dfm <- dfm_trim(buttigieg_moral_dfm, min_termfreq = 3)
buttigieg_moral_dfm <- `docnames<-`(buttigieg_moral_dfm, "buttigieg_moral_dfm")
klobuchar_moral_dfm <- dfm(klobuchar_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
klobuchar_moral_dfm <- dfm_trim(klobuchar_moral_dfm, min_termfreq = 3)
klobuchar_moral_dfm <- `docnames<-`(klobuchar_moral_dfm, "klobuchar_moral_dfm")
steyer_moral_dfm <- dfm(steyer_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
steyer_moral_dfm <- dfm_trim(steyer_moral_dfm, min_termfreq = 3)
steyer_moral_dfm <- `docnames<-`(steyer_moral_dfm, "steyer_moral_dfm")
yang_moral_dfm <- dfm(yang_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
yang_moral_dfm <- dfm_trim(yang_moral_dfm, min_termfreq = 3)
yang_moral_dfm <- `docnames<-`(yang_moral_dfm, "yang_moral_dfm")
harris_moral_dfm <- dfm(harris_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
harris_moral_dfm <- dfm_trim(harris_moral_dfm, min_termfreq = 3)
harris_moral_dfm <- `docnames<-`(harris_moral_dfm, "harris_moral_dfm")
booker_moral_dfm <- dfm(booker_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
booker_moral_dfm <- dfm_trim(booker_moral_dfm, min_termfreq = 3)
booker_moral_dfm <- `docnames<-`(booker_moral_dfm, "booker_moral_dfm")

gabbard_moral_dfm <- dfm(gabbard_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
gabbard_moral_dfm <- dfm_trim(gabbard_moral_dfm, min_termfreq = 3)
gabbard_moral_dfm <- `docnames<-`(gabbard_moral_dfm, "gabbard_moral_dfm")

castro_moral_dfm <- dfm(castro_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
castro_moral_dfm <- dfm_trim(castro_moral_dfm, min_termfreq = 3)
castro_moral_dfm <- `docnames<-`(castro_moral_dfm, "castro_moral_dfm")

orourke_moral_dfm <- dfm(orourke_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
orourke_moral_dfm <- dfm_trim(orourke_moral_dfm, min_termfreq = 3)
orourke_moral_dfm <- `docnames<-`(orourke_moral_dfm, "orourke_moral_dfm")

bloomberg_moral_dfm <- dfm(bloomberg_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
bloomberg_moral_dfm <- dfm_trim(bloomberg_moral_dfm, min_termfreq = 3)
bloomberg_moral_dfm <- `docnames<-`(bloomberg_moral_dfm, "bloomberg_moral_dfm")

bennet_moral_dfm <- dfm(bennet_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
bennet_moral_dfm <- dfm_trim(bennet_moral_dfm, min_termfreq = 3)
bennet_moral_dfm <- `docnames<-`(bennet_moral_dfm, "bennet_moral_dfm")

delaney_moral_dfm <- dfm(delaney_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
delaney_moral_dfm <- dfm_trim(delaney_moral_dfm, min_termfreq = 3)
delaney_moral_dfm <- `docnames<-`(delaney_moral_dfm, "delaney_moral_dfm")

williamson_moral_dfm <- dfm(williamson_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
williamson_moral_dfm <- dfm_trim(williamson_moral_dfm, min_termfreq = 3)
williamson_moral_dfm <- `docnames<-`(williamson_moral_dfm, "williamson_moral_dfm")

ryan_moral_dfm <- dfm(ryan_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
ryan_moral_dfm <- dfm_trim(ryan_moral_dfm, min_termfreq = 3)
ryan_moral_dfm <- `docnames<-`(ryan_moral_dfm, "ryan_moral_dfm")

deblasio_moral_dfm <- dfm(deblasio_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
deblasio_moral_dfm <- dfm_trim(deblasio_moral_dfm, min_termfreq = 3)
deblasio_moral_dfm <- `docnames<-`(deblasio_moral_dfm, "deblasio_moral_dfm")

gillibrand_moral_dfm <- dfm(gillibrand_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
gillibrand_moral_dfm <- dfm_trim(gillibrand_moral_dfm, min_termfreq = 3)
gillibrand_moral_dfm <- `docnames<-`(gillibrand_moral_dfm, "gillibrand_moral_dfm")

inslee_moral_dfm <- dfm(inslee_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
inslee_moral_dfm <- dfm_trim(inslee_moral_dfm, min_termfreq = 3)
inslee_moral_dfm <- `docnames<-`(inslee_moral_dfm, "inslee_moral_dfm")

hickenlooper_moral_dfm <- dfm(hickenlooper_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
hickenlooper_moral_dfm <- dfm_trim(hickenlooper_moral_dfm, min_termfreq = 3)
hickenlooper_moral_dfm <- `docnames<-`(hickenlooper_moral_dfm, "hickenlooper_moral_dfm")

bullock_moral_dfm <- dfm(bullock_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
bullock_moral_dfm <- dfm_trim(bullock_moral_dfm, min_termfreq = 3)
bullock_moral_dfm <- `docnames<-`(bullock_moral_dfm, "bullock_moral_dfm")

swalwell_moral_dfm <- dfm(swalwell_moral, remove_punct=TRUE, remove = stopwords(language = "en"))
swalwell_moral_dfm <- dfm_trim(swalwell_moral_dfm, min_termfreq = 3)
swalwell_moral_dfm <- `docnames<-`(swalwell_moral_dfm, "swalwell_moral_dfm")

#dems primary 2016
clinton_moral2016primary_dfm <- dfm(clinton_moral2016primary, remove_punct=TRUE, remove = stopwords(language = "en"))
clinton_moral2016primary_dfm <- dfm_trim(clinton_moral2016primary_dfm, min_termfreq = 3)
clinton_moral2016primary_dfm <- `docnames<-`(clinton_moral2016primary_dfm, "clinton_moral2016primary_dfm")

sanders_moral2016primary_dfm <- dfm(sanders_moral2016primary, remove_punct=TRUE, remove = stopwords(language = "en"))
sanders_moral2016primary_dfm <- dfm_trim(sanders_moral2016primary_dfm, min_termfreq = 3)
sanders_moral2016primary_dfm <- `docnames<-`(sanders_moral2016primary_dfm, "sanders_moral2016primary_dfm")

omalley_moral2016primary_dfm <- dfm(omalley_moral2016primary, remove_punct=TRUE, remove = stopwords(language = "en"))
omalley_moral2016primary_dfm <- dfm_trim(omalley_moral2016primary_dfm, min_termfreq = 3)
omalley_moral2016primary_dfm <- `docnames<-`(omalley_moral2016primary_dfm, "omalley_moral2016primary_dfm")

#GE 2016 & 2020
  #2016
clinton_moral2016GE_dfm <- dfm(clinton_moral2016GE, remove_punct=TRUE, remove = stopwords(language = "en"))
clinton_moral2016GE_dfm <- dfm_trim(clinton_moral2016GE_dfm, min_termfreq = 3)
clinton_moral2016GE_dfm <- `docnames<-`(clinton_moral2016GE_dfm, "clinton_moral2016GE_dfm")

trump_moral2016GE_dfm <- dfm(trump_moral2016GE, remove_punct=TRUE, remove = c("crooked", stopwords(language = "en")))
trump_moral2016GE_dfm <- dfm_trim(trump_moral2016GE_dfm, min_termfreq = 3)
trump_moral2016GE_dfm <- `docnames<-`(trump_moral2016GE_dfm, "trump_moral2016GE_dfm")

  #2020
trump_moral2020GE_dfm <- dfm(trump_moral2020GE, remove_punct=TRUE, remove = stopwords(language = "en"))
trump_moral2020GE_dfm <- dfm_trim(trump_moral2020GE_dfm, min_termfreq = 3)
trump_moral2020GE_dfm <- `docnames<-`(trump_moral2020GE_dfm, "trump_moral2020GE_dfm")

biden_moral2020GE_dfm <- dfm(biden_moral2020GE, remove_punct=TRUE, remove = stopwords(language = "en"))
biden_moral2020GE_dfm <- dfm_trim(biden_moral2020GE_dfm, min_termfreq = 3)
biden_moral2020GE_dfm <- `docnames<-`(biden_moral2020GE_dfm, "biden_moral2020GE_dfm")
```
Step 10 : Find "specific" moral terms by ranking all features by tf-idf frequency score
```{r}
#create combined dfm for 2016 primary 
   
trump_moral_dfm1 <- trump_moral_dfm
cruz_moral_dfm1 <- cruz_moral_dfm
rubio_moral_dfm1 <- rubio_moral_dfm
kasich_moral_dfm1 <- kasich_moral_dfm
carson_moral_dfm1 <- carson_moral_dfm
bush_moral_dfm1 <- bush_moral_dfm
paul_moral_dfm1 <- paul_moral_dfm
fiorina_moral_dfm1 <- fiorina_moral_dfm
graham_moral_dfm1 <- graham_moral_dfm
huckabee_moral_dfm1 <- huckabee_moral_dfm
 
#FINAL WEIGHTING; all data included, 26 dem dcuments 26 repub documents exluding 4 outliers, 2 dem and 2 repub. top 10 2016 repub primary candidates included twice to upsample.                          
bipartisan_moral2016primary_dfm <- rbind(trump_moral_dfm,
                                         trump_moral_dfm1,
                                         cruz_moral_dfm,
                                         cruz_moral_dfm1,
                                         rubio_moral_dfm,
                                         rubio_moral_dfm1,
                                         kasich_moral_dfm,
                                         kasich_moral_dfm1,
                                         carson_moral_dfm,
                                         carson_moral_dfm1,
                                         bush_moral_dfm,
                                         bush_moral_dfm1,
                                         paul_moral_dfm,
                                         paul_moral_dfm1,
                                         fiorina_moral_dfm,
                                         fiorina_moral_dfm1,
                                         graham_moral_dfm,
                                         graham_moral_dfm1,
                                         huckabee_moral_dfm,
                                         huckabee_moral_dfm1,
                                         walker_moral_dfm,
                                         jindal_moral_dfm,
                                         santorum_moral_dfm,
                                         pataki_moral_dfm,
                                         clinton_moral2016primary_dfm,
                                         sanders_moral2016primary_dfm,
                                         omalley_moral2016primary_dfm,
                                         biden_moral_dfm,
                                         buttigieg_moral_dfm,
                                         warren_moral_dfm,
                                         klobuchar_moral_dfm,
                                         warren_moral_dfm,
                                         harris_moral_dfm,
                                         booker_moral_dfm,
                                         steyer_moral_dfm,
                                         yang_moral_dfm,
                                         gabbard_moral_dfm,
                                         castro_moral_dfm,
                                         orourke_moral_dfm,
                                         bennet_moral_dfm,
                                         delaney_moral_dfm,
                                         williamson_moral_dfm,
                                         ryan_moral_dfm,
                                         gillibrand_moral_dfm,
                                         inslee_moral_dfm,
                                         hickenlooper_moral_dfm,
                                         bullock_moral_dfm,
                                         swalwell_moral_dfm,
                                         clinton_moral2016GE_dfm,
                                         trump_moral2020GE_dfm,
                                         biden_moral2020GE_dfm,
                                         trump_moral2016GE_dfm)


#lowercase and remove stopwords
bipartisan_moral2016primary_dfm <- dfm(bipartisan_moral2016primary_dfm, tolower = TRUE, remove = stopwords(language = "en"))
#plot unweighted rank/frequency distribution (power law)
plot(topfeatures(bipartisan_moral2016primary_dfm, n = 1000))

#weight by tf-idf
tfidf_bipartisan_moral2016primary_dfm <- dfm_tfidf(bipartisan_moral2016primary_dfm, scheme_tf = "prop")

#rank all features by tf-idf score
tfidf_topfeatures_moral2016primary <- as.data.frame(topfeatures(tfidf_bipartisan_moral2016primary_dfm, n=1000))
hist(tfidf_topfeatures_moral2016primary$`topfeatures(tfidf_bipartisan_moral2016primary_dfm, n = 1000)`)

#plot histogram tf-idf frequency distribution
ggplot(tfidf_topfeatures_moral2016primary, aes(x = `topfeatures(tfidf_bipartisan_moral2016primary_dfm, n = 1000)`)) + geom_histogram(color="black", fill="darkgrey", bins = 200) + ggtitle("TF-IDF Frequency Distribution of Moral Terms") + labs(y = "Count", x = "TF-IDF Frequency") + theme(plot.title = element_text(hjust = 0.5)) 

#+ geom_density(alpha=.2) 


#plot log(rank)-log(term frequency) graph showing moral language used by each candidate 
  #raw
zipf_moral <- tidy(bipartisan_moral2016primary_dfm) %>%
  group_by(document) %>%
  arrange(desc(count)) %>%
  mutate(rank = row_number(),
         total = sum(count),
         `term frequency` = count / total)
zipf_moral %>%
  ggplot(aes(rank, `term frequency`, color = document)) +
  geom_line(alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10() +
  ggtitle("Rank-Frequency Distribution of Moral Terms by Candidate") +
  labs(y= "log (Term Frequency)", x = "log (Term Rank)") +
  theme(plot.title = element_text(hjust = 0.5)) 
  
#, subtitle = ("Axis scaled logarithmically")

  #tf-idf
zipf_moral_tfidf <- tidy(tfidf_bipartisan_moral2016primary_dfm) %>%
  group_by(document) %>%
  arrange(desc(count)) %>%
  mutate(rank = row_number(),
         total = sum(count),
         `term frequency` = count / total)
h <- .0014
zipf_moral_tfidf %>%
  ggplot(aes(rank, `term frequency`, color = document)) +
  geom_line(alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10() + 
  geom_line(aes(y=.0014), color="black", show.legend = FALSE, linetype="dashed") + 
  geom_text(aes(0,h,label = "y = .0014", vjust = -1, hjust = -2), show.legend=FALSE, color = "black") +
  ggtitle("TF-IDF Rank-Frequency Distribution of Moral Terms by Candidate") +
  labs(y= "log (TF-IDF Term Frequency)", x = "log (Term Rank)") +
  theme(plot.title = element_text(hjust = 0.5))




#select filtering threshold
tfidf_topfeat_selected <- as.data.frame(topfeatures(tfidf_bipartisan_moral2016primary_dfm, n=575)) 

tfidf_topfeat_names <- as.character(row.names(tfidf_topfeat_selected))

#create txt file of selected terms to be used as new dictionary
bipartisan_toks_specific <- tokens(tfidf_topfeat_names)
sum(ntoken(bipartisan_toks_specific))
bipartisan_toks_specific <- as.character(bipartisan_toks_specific)
write(bipartisan_toks_specific, "specificmoral2016primary.txt")
```
Step 11: Construct new dictionary of "specific" terms
```{r}
#apply original mfd to list of extracted terms to see how the extracted terms are divided between categories 
specific_moral_terms <- readLines("specificmoral2016primary.txt")
specific_moral_terms_corpus <- corpus(specific_moral_terms)

#divide selected terms into 10 subcategories
toks_specific_moral <- tokens(specific_moral_terms_corpus)
  
  #care.virtue
extracted_toks_care.virtue <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$care.virtue, valuetype = "glob") 
extracted_toks_care.virtue <- as.character(extracted_toks_care.virtue)
  #care.vice
extracted_toks_care.vice <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$care.vice, valuetype = "glob") 
extracted_toks_care.vice <- as.character(extracted_toks_care.vice)
  
  #fairness.virtue
extracted_toks_fairness.virtue <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$fairness.virtue, valuetype = "glob") 
extracted_toks_fairness.virtue <- as.character(extracted_toks_fairness.virtue)
  #fairness.vice
extracted_toks_fairness.vice <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$fairness.vice, valuetype = "glob") 
extracted_toks_fairness.vice <- as.character(extracted_toks_fairness.vice)
  
  #loyalty.virtue
extracted_toks_loyalty.virtue <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$loyalty.virtue, valuetype = "glob") 
extracted_toks_loyalty.virtue <- as.character(extracted_toks_loyalty.virtue)
  #loyalty.vice
extracted_toks_loyalty.vice <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$loyalty.vice, valuetype = "glob") 
extracted_toks_loyalty.vice <- as.character(extracted_toks_loyalty.vice)
  
  #authority.virtue
extracted_toks_authority.virtue <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$authority.virtue, valuetype = "glob") 
extracted_toks_authority.virtue <- as.character(extracted_toks_authority.virtue)
  #authority.vice
extracted_toks_authority.vice <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$authority.vice, valuetype = "glob") 
extracted_toks_authority.vice <- as.character(extracted_toks_authority.vice)
  
  #sanctity.virtue
extracted_toks_sanctity.virtue <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$sanctity.virtue, valuetype = "glob") 
extracted_toks_sanctity.virtue <- as.character(extracted_toks_sanctity.virtue)
  #sanctity.vice
extracted_toks_sanctity.vice <- tokens_select(toks_specific_moral, pattern = data_dictionary_MFD$sanctity.vice, valuetype = "glob") 
extracted_toks_sanctity.vice <- as.character(extracted_toks_sanctity.vice)


#convert extracted lists to a format suitable for creation of sub-dictionaries 
  #care
extracted_care.virtue_list <- as.list(extracted_toks_care.virtue)
names(extracted_care.virtue_list) = extracted_toks_care.virtue

extracted_care.vice_list <- as.list(extracted_toks_care.vice)
names(extracted_care.vice_list) = extracted_toks_care.vice
  
  #fairness
extracted_fairness.virtue_list <- as.list(extracted_toks_fairness.virtue)
names(extracted_fairness.virtue_list) = extracted_toks_fairness.virtue

extracted_fairness.vice_list <- as.list(extracted_toks_fairness.vice)
names(extracted_fairness.vice_list) = extracted_toks_fairness.vice

  #loyalty 
extracted_loyalty.virtue_list <- as.list(extracted_toks_loyalty.virtue)
names(extracted_loyalty.virtue_list) = extracted_toks_loyalty.virtue

extracted_loyalty.vice_list <- as.list(extracted_toks_loyalty.vice)
names(extracted_loyalty.vice_list) = extracted_toks_loyalty.vice

  #authority
extracted_authority.virtue_list <- as.list(extracted_toks_authority.virtue)
names(extracted_authority.virtue_list) = extracted_toks_authority.virtue

extracted_authority.vice_list <- as.list(extracted_toks_authority.vice)
names(extracted_authority.vice_list) = extracted_toks_authority.vice

  #sanctity 
extracted_sanctity.virtue_list <- as.list(extracted_toks_sanctity.virtue)
names(extracted_sanctity.virtue_list) = extracted_toks_sanctity.virtue

extracted_sanctity.vice_list <- as.list(extracted_toks_sanctity.vice)
names(extracted_sanctity.vice_list) = extracted_toks_sanctity.vice

#create dictionary from extracted "specific" terms: 
extracted_dict <- dictionary(list(care.virtue_ex = extracted_care.virtue_list,
                                  care.vice_ex = extracted_care.vice_list,
                                  fairness.virtue_ex = extracted_fairness.virtue_list,
                                  fairness.vice_ex = extracted_fairness.vice_list,
                                  loyalty.virtue_ex = extracted_loyalty.virtue_list,
                                  loyalty.vice_ex = extracted_loyalty.vice_list,
                                  authority.virtue_ex = extracted_authority.virtue_list,
                                  authority.vice_ex = extracted_authority.vice_list,
                                  sanctity.virtue_ex = extracted_sanctity.virtue_list,
                                  sanctity.vice_ex = extracted_sanctity.vice_list))
```


APPLY WEIGHTED & FILTERED DICTIONARY 
Step 12: Apply new "specific" dictionary to each 2020 DEMOCRATIC PRIMARY candidate corpus
```{r}
#SANDERS
extracted_moral_toks_sanders <- tokens_select(toks_sanders, pattern = extracted_dict, valuetype = "glob")
sanders_moral_extracted <- as.character(extracted_moral_toks_sanders)
sum(ntoken(sanders_moral_extracted))

sanders_moral_dfm_extracted <- dfm(sanders_moral_extracted, remove_punct=TRUE, remove = c("damn", "pandemic"))
sanders_moral_dfm_extracted <-dfm_weight(sanders_moral_dfm_extracted, scheme = "prop")

dict_moral_sanders_extracted <- dfm_lookup(sanders_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_sanders_extracted <- as.data.frame(dict_moral_sanders_extracted)

sum(data_moral_sanders_extracted$care.virtue) 
sum(data_moral_sanders_extracted$fairness.virtue) 
sum(data_moral_sanders_extracted$loyalty.virtue) 
sum(data_moral_sanders_extracted$authority.virtue) 
sum(data_moral_sanders_extracted$sanctity.virtue) 
sum(data_moral_sanders_extracted$care.vice) 
sum(data_moral_sanders_extracted$fairness.vice) 
sum(data_moral_sanders_extracted$loyalty.vice) 
sum(data_moral_sanders_extracted$authority.vice) 
sum(data_moral_sanders_extracted$sanctity.vice) 
2739/7635
826/7635
1560/7635
599/7635
274/7635
774/7635
329/7635
32/7635
83/7635
388/7635

#BUTTIGIEG
extracted_moral_toks_buttigieg <- tokens_select(toks_buttigieg, pattern = extracted_dict, valuetype = "glob")
buttigieg_moral_extracted <- as.character(extracted_moral_toks_buttigieg)
sum(ntoken(buttigieg_moral_extracted))

buttigieg_moral_dfm_extracted <- dfm(buttigieg_moral_extracted, remove_punct=TRUE)
buttigieg_moral_dfm_extracted <-dfm_weight(buttigieg_moral_dfm_extracted, scheme = "prop")

dict_moral_buttigieg_extracted <- dfm_lookup(buttigieg_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_buttigieg_extracted <- as.data.frame(dict_moral_buttigieg_extracted)

sum(data_moral_buttigieg_extracted$care.virtue) 
sum(data_moral_buttigieg_extracted$fairness.virtue) 
sum(data_moral_buttigieg_extracted$loyalty.virtue) 
sum(data_moral_buttigieg_extracted$authority.virtue) 
sum(data_moral_buttigieg_extracted$sanctity.virtue) 
sum(data_moral_buttigieg_extracted$care.vice) 
sum(data_moral_buttigieg_extracted$fairness.vice) 
sum(data_moral_buttigieg_extracted$loyalty.vice) 
sum(data_moral_buttigieg_extracted$authority.vice) 
sum(data_moral_buttigieg_extracted$sanctity.vice) 
838/2777
330/2777
770/2777
259/2777
137/2777
264/2777
116/2777
5/2777
22/2777
70/2777

buttigieg_loyalty.virtue <- tokens_select(toks_buttigieg, pattern = extracted_dict$loyalty.virtue_ex, valuetype = "glob")
buttigieg_loyalty.virtue <- as.character(buttigieg_loyalty.virtue)

#BIDEN
extracted_moral_toks_biden <- tokens_select(toks_biden, pattern = extracted_dict, valuetype = "glob")
biden_moral_extracted <- as.character(extracted_moral_toks_biden)
sum(ntoken(biden_moral_extracted))

biden_moral_dfm_extracted <- dfm(biden_moral_extracted, remove_punct=TRUE)
biden_moral_dfm_extracted <-dfm_weight(biden_moral_dfm_extracted, scheme = "prop")

dict_moral_biden_extracted <- dfm_lookup(biden_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_biden_extracted <- as.data.frame(dict_moral_biden_extracted)

sum(data_moral_biden_extracted$care.virtue) 
sum(data_moral_biden_extracted$fairness.virtue) 
sum(data_moral_biden_extracted$loyalty.virtue) 
sum(data_moral_biden_extracted$authority.virtue) 
sum(data_moral_biden_extracted$sanctity.virtue) 
sum(data_moral_biden_extracted$care.vice)
sum(data_moral_biden_extracted$fairness.vice) 
sum(data_moral_biden_extracted$loyalty.vice)
sum(data_moral_biden_extracted$authority.vice) 
sum(data_moral_biden_extracted$sanctity.vice) 
1078/3960
385/3960
923/3960
358/3960
337/3960
573/3960
99/3960
13/3960
28/3960
239/3960

biden_sanctity.virtue <- tokens_select(toks_biden, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
biden_sanctity.virtue <- as.character(biden_sanctity.virtue)

#WARREN
extracted_moral_toks_warren <- tokens_select(toks_warren, pattern = extracted_dict, valuetype = "glob")
warren_moral_extracted <- as.character(extracted_moral_toks_warren)
sum(ntoken(warren_moral_extracted))

warren_moral_dfm_extracted <- dfm(warren_moral_extracted, remove_punct=TRUE)
warren_moral_dfm_extracted <-dfm_weight(warren_moral_dfm_extracted, scheme = "prop")

dict_moral_warren_extracted <- dfm_lookup(warren_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_warren_extracted <- as.data.frame(dict_moral_warren_extracted)

sum(data_moral_warren_extracted$care.virtue) 
sum(data_moral_warren_extracted$fairness.virtue) 
sum(data_moral_warren_extracted$loyalty.virtue) 
sum(data_moral_warren_extracted$authority.virtue)
sum(data_moral_warren_extracted$sanctity.virtue)
sum(data_moral_warren_extracted$care.vice)
sum(data_moral_warren_extracted$fairness.vice) 
sum(data_moral_warren_extracted$loyalty.vice)
sum(data_moral_warren_extracted$authority.vice) 
sum(data_moral_warren_extracted$sanctity.vice)
2637/9415
1267/9415
1742/9415
696/9415
311/9415
1612/9415
520/9415
5/9415
85/9415
746/9415

warren_sanctity.virtue <- tokens_select(toks_warren, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
warren_sanctity.virtue <- as.character(warren_sanctity.virtue)

#KLOBUCHAR
extracted_moral_toks_klobuchar <- tokens_select(toks_klobuchar, pattern = extracted_dict, valuetype = "glob")
klobuchar_moral_extracted <- as.character(extracted_moral_toks_klobuchar)
sum(ntoken(klobuchar_moral_extracted))

klobuchar_moral_dfm_extracted <- dfm(klobuchar_moral_extracted, remove_punct=TRUE)
klobuchar_moral_dfm_extracted <-dfm_weight(klobuchar_moral_dfm_extracted, scheme = "prop")

dict_moral_klobuchar_extracted <- dfm_lookup(klobuchar_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_klobuchar_extracted <- as.data.frame(dict_moral_klobuchar_extracted)

sum(data_moral_klobuchar_extracted$care.virtue)
sum(data_moral_klobuchar_extracted$fairness.virtue) 
sum(data_moral_klobuchar_extracted$loyalty.virtue) 
sum(data_moral_klobuchar_extracted$authority.virtue) 
sum(data_moral_klobuchar_extracted$sanctity.virtue) 
sum(data_moral_klobuchar_extracted$care.vice) 
sum(data_moral_klobuchar_extracted$fairness.vice) 
sum(data_moral_klobuchar_extracted$loyalty.vice) 
sum(data_moral_klobuchar_extracted$authority.vice) 
sum(data_moral_klobuchar_extracted$sanctity.vice) 
761/2569
329/2569
567/2569
301/2569
108/2569
289/2569
56/2569
5/2569
28/2569
171/2569

klobuchar_authority.virtue <- tokens_select(toks_klobuchar, pattern = extracted_dict$authority.virtue_ex, valuetype = "glob")
klobuchar_authority.virtue <- as.character(klobuchar_authority.virtue)

#YANG
extracted_moral_toks_yang <- tokens_select(toks_yang, pattern = extracted_dict, valuetype = "glob")
yang_moral_extracted <- as.character(extracted_moral_toks_yang)
sum(ntoken(yang_moral_extracted))

yang_moral_dfm_extracted <- dfm(yang_moral_extracted, remove_punct=TRUE)
yang_moral_dfm_extracted <-dfm_weight(yang_moral_dfm_extracted, scheme = "prop")

dict_moral_yang_extracted <- dfm_lookup(yang_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_yang_extracted <- as.data.frame(dict_moral_yang_extracted)

sum(data_moral_yang_extracted$care.virtue) 
sum(data_moral_yang_extracted$fairness.virtue) 
sum(data_moral_yang_extracted$loyalty.virtue) 
sum(data_moral_yang_extracted$authority.virtue)
sum(data_moral_yang_extracted$sanctity.virtue)
sum(data_moral_yang_extracted$care.vice) 
sum(data_moral_yang_extracted$fairness.vice) 
sum(data_moral_yang_extracted$loyalty.vice) 
sum(data_moral_yang_extracted$authority.vice) 
sum(data_moral_yang_extracted$sanctity.vice)
756/2417
161/2417
644/2417
298/2417
162/2417
210/2417
53/2417
9/2417
5/2417
148/2417

yang_sanctity.virtue <- tokens_select(toks_yang, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
yang_sanctity.virtue <- as.character(yang_sanctity.virtue)

#STEYER
extracted_moral_toks_steyer <- tokens_select(toks_steyer, pattern = extracted_dict, valuetype = "glob")
steyer_moral_extracted <- as.character(extracted_moral_toks_steyer)
sum(ntoken(steyer_moral_extracted))

steyer_moral_dfm_extracted <- dfm(steyer_moral_extracted, remove_punct=TRUE)
steyer_moral_dfm_extracted <-dfm_weight(steyer_moral_dfm_extracted, scheme = "prop")

dict_moral_steyer_extracted <- dfm_lookup(steyer_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_steyer_extracted <- as.data.frame(dict_moral_steyer_extracted)

sum(data_moral_steyer_extracted$care.virtue) 
sum(data_moral_steyer_extracted$fairness.virtue)  
sum(data_moral_steyer_extracted$loyalty.virtue) 
sum(data_moral_steyer_extracted$authority.virtue) 
sum(data_moral_steyer_extracted$sanctity.virtue)  
sum(data_moral_steyer_extracted$care.vice) 
sum(data_moral_steyer_extracted$fairness.vice)  
sum(data_moral_steyer_extracted$loyalty.vice) 
sum(data_moral_steyer_extracted$authority.vice)
sum(data_moral_steyer_extracted$sanctity.vice)
1070/3373
400/3373
476/3373
365/3373
110/3373
364/3373
437/3373
26/3373
38/3373
132/3373

steyer_fairness.vice <- tokens_select(toks_steyer, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
steyer_fairness.vice <- as.character(steyer_fairness.vice)

#HARRIS
extracted_moral_toks_harris <- tokens_select(toks_harris, pattern = extracted_dict, valuetype = "glob")
harris_moral_extracted <- as.character(extracted_moral_toks_harris)
sum(ntoken(harris_moral_extracted))

harris_moral_dfm_extracted <- dfm(harris_moral_extracted, remove_punct=TRUE)
harris_moral_dfm_extracted <-dfm_weight(harris_moral_dfm_extracted, scheme = "prop")

dict_moral_harris_extracted <- dfm_lookup(harris_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_harris_extracted <- as.data.frame(dict_moral_harris_extracted)

sum(data_moral_harris_extracted$care.virtue)   
sum(data_moral_harris_extracted$fairness.virtue)  
sum(data_moral_harris_extracted$loyalty.virtue) 
sum(data_moral_harris_extracted$authority.virtue) 
sum(data_moral_harris_extracted$sanctity.virtue) 
sum(data_moral_harris_extracted$care.vice)  
sum(data_moral_harris_extracted$fairness.vice)   
sum(data_moral_harris_extracted$loyalty.vice) 
sum(data_moral_harris_extracted$authority.vice)  
sum(data_moral_harris_extracted$sanctity.vice) 
1421/4697
782/4697
787/4697
356/4697
233/4697
811/4697
188/4697
4/4697
41/4697
163/4697

harris_fairness.vice <- tokens_select(toks_harris, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
harris_fairness.vice <- as.character(harris_fairness.vice)

#BOOKER
extracted_moral_toks_booker <- tokens_select(toks_booker, pattern = extracted_dict, valuetype = "glob")
booker_moral_extracted <- as.character(extracted_moral_toks_booker)
sum(ntoken(booker_moral_extracted))

booker_moral_dfm_extracted <- dfm(booker_moral_extracted, remove_punct=TRUE)
booker_moral_dfm_extracted <-dfm_weight(booker_moral_dfm_extracted, scheme = "prop")

dict_moral_booker_extracted <- dfm_lookup(booker_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_booker_extracted <- as.data.frame(dict_moral_booker_extracted)

sum(data_moral_booker_extracted$care.virtue)  
sum(data_moral_booker_extracted$fairness.virtue)  
sum(data_moral_booker_extracted$loyalty.virtue)  
sum(data_moral_booker_extracted$authority.virtue)  
sum(data_moral_booker_extracted$sanctity.virtue) 
sum(data_moral_booker_extracted$care.vice)  
sum(data_moral_booker_extracted$fairness.vice)  
sum(data_moral_booker_extracted$loyalty.vice)  
sum(data_moral_booker_extracted$authority.vice) 
sum(data_moral_booker_extracted$sanctity.vice) 
833/3259
520/3259
687/3259
243/3259
210/3259
490/3259
137/3259
4/3259
21/3259
155/3259

booker_sanctity.virtue <- tokens_select(toks_booker, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
booker_sanctity.virtue <- as.character(booker_sanctity.virtue)

#GABBARD
extracted_moral_toks_gabbard <- tokens_select(toks_gabbard, pattern = extracted_dict, valuetype = "glob")
gabbard_moral_extracted <- as.character(extracted_moral_toks_gabbard)
sum(ntoken(gabbard_moral_extracted))

gabbard_moral_dfm_extracted <- dfm(gabbard_moral_extracted, remove_punct=TRUE)
gabbard_moral_dfm_extracted <-dfm_weight(gabbard_moral_dfm_extracted, scheme = "prop")

dict_moral_gabbard_extracted <- dfm_lookup(gabbard_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_gabbard_extracted <- as.data.frame(dict_moral_gabbard_extracted)

sum(data_moral_gabbard_extracted$care.virtue) 
sum(data_moral_gabbard_extracted$fairness.virtue) 
sum(data_moral_gabbard_extracted$loyalty.virtue) 
sum(data_moral_gabbard_extracted$authority.virtue) 
sum(data_moral_gabbard_extracted$sanctity.virtue) 
sum(data_moral_gabbard_extracted$care.vice)
sum(data_moral_gabbard_extracted$fairness.vice) 
sum(data_moral_gabbard_extracted$loyalty.vice)
sum(data_moral_gabbard_extracted$authority.vice) 
sum(data_moral_gabbard_extracted$sanctity.vice) 
378/1845
117/1845
606/1845
246/1845
132/1845
202/1845
37/1845
7/1845
18/1845
139/1845

gabbard_sanctity.virtue <- tokens_select(toks_gabbard, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
gabbard_sanctity.virtue <- as.character(gabbard_sanctity.virtue)

#CASTRO
extracted_moral_toks_castro <- tokens_select(toks_castro, pattern = extracted_dict, valuetype = "glob")
castro_moral_extracted <- as.character(extracted_moral_toks_castro)
sum(ntoken(castro_moral_extracted))

castro_moral_dfm_extracted <- dfm(castro_moral_extracted, remove_punct=TRUE)
castro_moral_dfm_extracted <-dfm_weight(castro_moral_dfm_extracted, scheme = "prop")

dict_moral_castro_extracted <- dfm_lookup(castro_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_castro_extracted <- as.data.frame(dict_moral_castro_extracted)

sum(data_moral_castro_extracted$care.virtue)
sum(data_moral_castro_extracted$fairness.virtue) 
sum(data_moral_castro_extracted$loyalty.virtue) 
sum(data_moral_castro_extracted$authority.virtue) 
sum(data_moral_castro_extracted$sanctity.virtue) 
sum(data_moral_castro_extracted$care.vice)
sum(data_moral_castro_extracted$fairness.vice) 
sum(data_moral_castro_extracted$loyalty.vice)
sum(data_moral_castro_extracted$authority.vice) 
sum(data_moral_castro_extracted$sanctity.vice) 
888/3641
467/3641
801/3641
493/3641
162/3641
638/3641
151/3641
4/3641
43/3641
95/3641

castro_sanctity.virtue <- tokens_select(toks_castro, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
castro_sanctity.virtue <- as.character(castro_sanctity.virtue)

#O'ROURKE
extracted_moral_toks_orourke <- tokens_select(toks_orourke, pattern = extracted_dict, valuetype = "glob")
orourke_moral_extracted <- as.character(extracted_moral_toks_orourke)
sum(ntoken(orourke_moral_extracted))

orourke_moral_dfm_extracted <- dfm(orourke_moral_extracted, remove_punct=TRUE)
orourke_moral_dfm_extracted <-dfm_weight(orourke_moral_dfm_extracted, scheme = "prop")

dict_moral_orourke_extracted <- dfm_lookup(orourke_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_orourke_extracted <- as.data.frame(dict_moral_orourke_extracted)

sum(data_moral_orourke_extracted$care.virtue) 
sum(data_moral_orourke_extracted$fairness.virtue) 
sum(data_moral_orourke_extracted$loyalty.virtue) 
sum(data_moral_orourke_extracted$authority.virtue) 
sum(data_moral_orourke_extracted$sanctity.virtue) 
sum(data_moral_orourke_extracted$care.vice)
sum(data_moral_orourke_extracted$fairness.vice) 
sum(data_moral_orourke_extracted$loyalty.vice)
sum(data_moral_orourke_extracted$authority.vice) 
sum(data_moral_orourke_extracted$sanctity.vice) 
924/4012
589/4012
989/4012
251/4012
165/4012
704/4012
202/4012
4/4012
49/4012
192/4012

orourke_sanctity.virtue <- tokens_select(toks_orourke, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
orourke_sanctity.virtue <- as.character(orourke_sanctity.virtue)

#BENNET
extracted_moral_toks_bennet <- tokens_select(toks_bennet, pattern = extracted_dict, valuetype = "glob")
bennet_moral_extracted <- as.character(extracted_moral_toks_bennet)
sum(ntoken(bennet_moral_extracted))

bennet_moral_dfm_extracted <- dfm(bennet_moral_extracted, remove_punct=TRUE)
bennet_moral_dfm_extracted <-dfm_weight(bennet_moral_dfm_extracted, scheme = "prop")

dict_moral_bennet_extracted <- dfm_lookup(bennet_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_bennet_extracted <- as.data.frame(dict_moral_bennet_extracted)

sum(data_moral_bennet_extracted$care.virtue) 
sum(data_moral_bennet_extracted$fairness.virtue) 
sum(data_moral_bennet_extracted$loyalty.virtue) 
sum(data_moral_bennet_extracted$authority.virtue) 
sum(data_moral_bennet_extracted$sanctity.virtue) 
sum(data_moral_bennet_extracted$care.vice)
sum(data_moral_bennet_extracted$fairness.vice) 
sum(data_moral_bennet_extracted$loyalty.vice)
sum(data_moral_bennet_extracted$authority.vice) 
sum(data_moral_bennet_extracted$sanctity.vice) 
735/2119
202/2119
540/2119
194/2119
77/2119
201/2119
73/2119
3/2119
25/2119
98/2119

bennet_sanctity.virtue <- tokens_select(toks_bennet, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
bennet_sanctity.virtue <- as.character(bennet_sanctity.virtue)

#DELANEY
extracted_moral_toks_delaney <- tokens_select(toks_delaney, pattern = extracted_dict, valuetype = "glob")
delaney_moral_extracted <- as.character(extracted_moral_toks_delaney)
sum(ntoken(delaney_moral_extracted))

delaney_moral_dfm_extracted <- dfm(delaney_moral_extracted, remove_punct=TRUE)
delaney_moral_dfm_extracted <-dfm_weight(delaney_moral_dfm_extracted, scheme = "prop")

dict_moral_delaney_extracted <- dfm_lookup(delaney_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_delaney_extracted <- as.data.frame(dict_moral_delaney_extracted)

sum(data_moral_delaney_extracted$care.virtue) 
sum(data_moral_delaney_extracted$fairness.virtue) 
sum(data_moral_delaney_extracted$loyalty.virtue) 
sum(data_moral_delaney_extracted$authority.virtue) 
sum(data_moral_delaney_extracted$sanctity.virtue) 
sum(data_moral_delaney_extracted$care.vice)
sum(data_moral_delaney_extracted$fairness.vice) 
sum(data_moral_delaney_extracted$loyalty.vice)
sum(data_moral_delaney_extracted$authority.vice) 
sum(data_moral_delaney_extracted$sanctity.vice) 
1415/4593
426/4593
1093/4593
525/4593
341/4593
494/4593
123/4593
13/4593
50/4593
177/4593

delaney_sanctity.virtue <- tokens_select(toks_delaney, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
delaney_sanctity.virtue <- as.character(delaney_sanctity.virtue)

#RYAN
extracted_moral_toks_ryan <- tokens_select(toks_ryan, pattern = extracted_dict, valuetype = "glob")
ryan_moral_extracted <- as.character(extracted_moral_toks_ryan)
sum(ntoken(ryan_moral_extracted))

ryan_moral_dfm_extracted <- dfm(ryan_moral_extracted, remove_punct=TRUE)
ryan_moral_dfm_extracted <-dfm_weight(ryan_moral_dfm_extracted, scheme = "prop")

dict_moral_ryan_extracted <- dfm_lookup(ryan_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_ryan_extracted <- as.data.frame(dict_moral_ryan_extracted)

sum(data_moral_ryan_extracted$care.virtue) 
sum(data_moral_ryan_extracted$fairness.virtue) 
sum(data_moral_ryan_extracted$loyalty.virtue) 
sum(data_moral_ryan_extracted$authority.virtue) 
sum(data_moral_ryan_extracted$sanctity.virtue) 
sum(data_moral_ryan_extracted$care.vice)
sum(data_moral_ryan_extracted$fairness.vice) 
sum(data_moral_ryan_extracted$loyalty.vice)
sum(data_moral_ryan_extracted$authority.vice) 
sum(data_moral_ryan_extracted$sanctity.vice) 
719/1758
87/1758
383/1758
127/1758
144/1758
204/1758
37/1758
1/1758
5/1758
81/1758

ryan_sanctity.virtue <- tokens_select(toks_ryan, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
ryan_sanctity.virtue <- as.character(ryan_sanctity.virtue)

#GILLIBRAND
extracted_moral_toks_gillibrand <- tokens_select(toks_gillibrand, pattern = extracted_dict, valuetype = "glob")
gillibrand_moral_extracted <- as.character(extracted_moral_toks_gillibrand)
sum(ntoken(gillibrand_moral_extracted))

gillibrand_moral_dfm_extracted <- dfm(gillibrand_moral_extracted, remove_punct=TRUE)
gillibrand_moral_dfm_extracted <-dfm_weight(gillibrand_moral_dfm_extracted, scheme = "prop")

dict_moral_gillibrand_extracted <- dfm_lookup(gillibrand_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_gillibrand_extracted <- as.data.frame(dict_moral_gillibrand_extracted)

sum(data_moral_gillibrand_extracted$care.virtue) 
sum(data_moral_gillibrand_extracted$fairness.virtue) 
sum(data_moral_gillibrand_extracted$loyalty.virtue) 
sum(data_moral_gillibrand_extracted$authority.virtue) 
sum(data_moral_gillibrand_extracted$sanctity.virtue) 
sum(data_moral_gillibrand_extracted$care.vice)
sum(data_moral_gillibrand_extracted$fairness.vice) 
sum(data_moral_gillibrand_extracted$loyalty.vice)
sum(data_moral_gillibrand_extracted$authority.vice) 
sum(data_moral_gillibrand_extracted$sanctity.vice) 
688/2054
348/2054
216/2054
158/2054
84/2054
386/2054
65/2054
0/2054
14/2054
131/2054

gillibrand_sanctity.virtue <- tokens_select(toks_gillibrand, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
gillibrand_sanctity.virtue <- as.character(gillibrand_sanctity.virtue)

#INSLEE
extracted_moral_toks_inslee <- tokens_select(toks_inslee, pattern = extracted_dict, valuetype = "glob")
inslee_moral_extracted <- as.character(extracted_moral_toks_inslee)
sum(ntoken(inslee_moral_extracted))

inslee_moral_dfm_extracted <- dfm(inslee_moral_extracted, remove_punct=TRUE)
inslee_moral_dfm_extracted <-dfm_weight(inslee_moral_dfm_extracted, scheme = "prop")

dict_moral_inslee_extracted <- dfm_lookup(inslee_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_inslee_extracted <- as.data.frame(dict_moral_inslee_extracted)

sum(data_moral_inslee_extracted$care.virtue) 
sum(data_moral_inslee_extracted$fairness.virtue) 
sum(data_moral_inslee_extracted$loyalty.virtue) 
sum(data_moral_inslee_extracted$authority.virtue) 
sum(data_moral_inslee_extracted$sanctity.virtue) 
sum(data_moral_inslee_extracted$care.vice)
sum(data_moral_inslee_extracted$fairness.vice) 
sum(data_moral_inslee_extracted$loyalty.vice)
sum(data_moral_inslee_extracted$authority.vice) 
sum(data_moral_inslee_extracted$sanctity.vice) 
463/2113
238/2113
443/2113
250/2113
248/2113
307/2113
98/2113
2/2113
25/2113
75/2113

inslee_sanctity.virtue <- tokens_select(toks_inslee, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
inslee_sanctity.virtue <- as.character(inslee_sanctity.virtue)

#HICKENLOOPER
extracted_moral_toks_hickenlooper <- tokens_select(toks_hickenlooper, pattern = extracted_dict, valuetype = "glob")
hickenlooper_moral_extracted <- as.character(extracted_moral_toks_hickenlooper)
sum(ntoken(hickenlooper_moral_extracted))

hickenlooper_moral_dfm_extracted <- dfm(hickenlooper_moral_extracted, remove_punct=TRUE)
hickenlooper_moral_dfm_extracted <-dfm_weight(hickenlooper_moral_dfm_extracted, scheme = "prop")

dict_moral_hickenlooper_extracted <- dfm_lookup(hickenlooper_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_hickenlooper_extracted <- as.data.frame(dict_moral_hickenlooper_extracted)

sum(data_moral_hickenlooper_extracted$care.virtue) 
sum(data_moral_hickenlooper_extracted$fairness.virtue) 
sum(data_moral_hickenlooper_extracted$loyalty.virtue) 
sum(data_moral_hickenlooper_extracted$authority.virtue) 
sum(data_moral_hickenlooper_extracted$sanctity.virtue) 
sum(data_moral_hickenlooper_extracted$care.vice)
sum(data_moral_hickenlooper_extracted$fairness.vice) 
sum(data_moral_hickenlooper_extracted$loyalty.vice)
sum(data_moral_hickenlooper_extracted$authority.vice) 
sum(data_moral_hickenlooper_extracted$sanctity.vice) 
304/1156
125/1156
246/1156
212/1156
49/1156
162/1156
30/1156
2/1156
6/1156
30/1156

hickenlooper_sanctity.virtue <- tokens_select(toks_hickenlooper, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
hickenlooper_sanctity.virtue <- as.character(hickenlooper_sanctity.virtue)

#BULLOCK
extracted_moral_toks_bullock <- tokens_select(toks_bullock, pattern = extracted_dict, valuetype = "glob")
bullock_moral_extracted <- as.character(extracted_moral_toks_bullock)
sum(ntoken(bullock_moral_extracted))

bullock_moral_dfm_extracted <- dfm(bullock_moral_extracted, remove_punct=TRUE)
bullock_moral_dfm_extracted <-dfm_weight(bullock_moral_dfm_extracted, scheme = "prop")

dict_moral_bullock_extracted <- dfm_lookup(bullock_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_bullock_extracted <- as.data.frame(dict_moral_bullock_extracted)

sum(data_moral_bullock_extracted$care.virtue) 
sum(data_moral_bullock_extracted$fairness.virtue) 
sum(data_moral_bullock_extracted$loyalty.virtue) 
sum(data_moral_bullock_extracted$authority.virtue) 
sum(data_moral_bullock_extracted$sanctity.virtue) 
sum(data_moral_bullock_extracted$care.vice)
sum(data_moral_bullock_extracted$fairness.vice) 
sum(data_moral_bullock_extracted$loyalty.vice)
sum(data_moral_bullock_extracted$authority.vice) 
sum(data_moral_bullock_extracted$sanctity.vice) 
391/1934
357/1934
404/1934
326/1934
33/1934
224/1934
35/1934
2/1934
13/1934
166/1934

bullock_sanctity.virtue <- tokens_select(toks_bullock, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
bullock_sanctity.virtue <- as.character(bullock_sanctity.virtue)

#SWALWELL
extracted_moral_toks_swalwell <- tokens_select(toks_swalwell, pattern = extracted_dict, valuetype = "glob")
swalwell_moral_extracted <- as.character(extracted_moral_toks_swalwell)
sum(ntoken(swalwell_moral_extracted))

swalwell_moral_dfm_extracted <- dfm(swalwell_moral_extracted, remove_punct=TRUE)
swalwell_moral_dfm_extracted <-dfm_weight(swalwell_moral_dfm_extracted, scheme = "prop")

dict_moral_swalwell_extracted <- dfm_lookup(swalwell_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_swalwell_extracted <- as.data.frame(dict_moral_swalwell_extracted)

sum(data_moral_swalwell_extracted$care.virtue) 
sum(data_moral_swalwell_extracted$fairness.virtue) 
sum(data_moral_swalwell_extracted$loyalty.virtue) 
sum(data_moral_swalwell_extracted$authority.virtue) 
sum(data_moral_swalwell_extracted$sanctity.virtue) 
sum(data_moral_swalwell_extracted$care.vice)
sum(data_moral_swalwell_extracted$fairness.vice) 
sum(data_moral_swalwell_extracted$loyalty.vice)
sum(data_moral_swalwell_extracted$authority.vice) 
sum(data_moral_swalwell_extracted$sanctity.vice) 
239/960
97/960
141/960
83/960
46/960
278/960
25/960
4/960
18/960
46/960

swalwell_sanctity.virtue <- tokens_select(toks_swalwell, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
swalwell_sanctity.virtue <- as.character(swalwell_sanctity.virtue)

#WILLIAMSON
extracted_moral_toks_williamson <- tokens_select(toks_williamson, pattern = extracted_dict, valuetype = "glob")
williamson_moral_extracted <- as.character(extracted_moral_toks_williamson)
sum(ntoken(williamson_moral_extracted))

williamson_moral_dfm_extracted <- dfm(williamson_moral_extracted, remove_punct=TRUE)
williamson_moral_dfm_extracted <-dfm_weight(williamson_moral_dfm_extracted, scheme = "prop")

dict_moral_williamson_extracted <- dfm_lookup(williamson_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_williamson_extracted <- as.data.frame(dict_moral_williamson_extracted)

sum(data_moral_williamson_extracted$care.virtue) 
sum(data_moral_williamson_extracted$fairness.virtue) 
sum(data_moral_williamson_extracted$loyalty.virtue) 
sum(data_moral_williamson_extracted$authority.virtue) 
sum(data_moral_williamson_extracted$sanctity.virtue) 
sum(data_moral_williamson_extracted$care.vice)
sum(data_moral_williamson_extracted$fairness.vice) 
sum(data_moral_williamson_extracted$loyalty.vice)
sum(data_moral_williamson_extracted$authority.vice) 
sum(data_moral_williamson_extracted$sanctity.vice) 
744/2684
256/2684
492/2684
334/2684
345/2684
301/2684
103/2684
0/2684
26/2684
131/2684

williamson_sanctity.virtue <- tokens_select(toks_williamson, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
williamson_sanctity.virtue <- as.character(williamson_sanctity.virtue)
```
Step 13: Apply new "specific" dictionary to each 2016 REPUBLICAN PRIMARY candidate corpus
```{r}
#TRUMP
extracted_moral_toks_trump <- tokens_select(toks_trump, pattern = extracted_dict, valuetype = "glob")
trump_moral_extracted <- as.character(extracted_moral_toks_trump)
sum(ntoken(trump_moral_extracted))

trump_moral_dfm_extracted <- dfm(trump_moral_extracted, remove_punct=TRUE)
trump_moral_dfm_extracted <-dfm_weight(trump_moral_dfm_extracted, scheme = "prop")

dict_moral_trump_extracted <- dfm_lookup(trump_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_trump_extracted <- as.data.frame(dict_moral_trump_extracted)

sum(data_moral_trump_extracted$care.virtue) 
sum(data_moral_trump_extracted$fairness.virtue)
sum(data_moral_trump_extracted$loyalty.virtue) 
sum(data_moral_trump_extracted$authority.virtue) 
sum(data_moral_trump_extracted$sanctity.virtue)
sum(data_moral_trump_extracted$care.vice) 
sum(data_moral_trump_extracted$fairness.vice)
sum(data_moral_trump_extracted$loyalty.vice) 
sum(data_moral_trump_extracted$authority.vice) 
sum(data_moral_trump_extracted$sanctity.vice) 
227/1678
125/1678
228/1678
330/1678
129/1678
197/1678
210/1678
19/1678
125/1678
105/1678

trump_fairness.vice <- tokens_select(extracted_moral_toks_trump, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
trump_fairness.vice <- as.character(trump_fairness.vice)

#CRUZ
extracted_moral_toks_cruz <- tokens_select(toks_cruz, pattern = extracted_dict, valuetype = "glob")
cruz_moral_extracted <- as.character(extracted_moral_toks_cruz)
sum(ntoken(cruz_moral_extracted))

cruz_moral_dfm_extracted <- dfm(cruz_moral_extracted, remove_punct=TRUE)
cruz_moral_dfm_extracted <-dfm_weight(cruz_moral_dfm_extracted, scheme = "prop")

dict_moral_cruz_extracted <- dfm_lookup(cruz_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_cruz_extracted <- as.data.frame(dict_moral_cruz_extracted)

sum(data_moral_cruz_extracted$care.virtue) 
sum(data_moral_cruz_extracted$fairness.virtue) 
sum(data_moral_cruz_extracted$loyalty.virtue) 
sum(data_moral_cruz_extracted$authority.virtue) 
sum(data_moral_cruz_extracted$sanctity.virtue) 
sum(data_moral_cruz_extracted$care.vice) 
sum(data_moral_cruz_extracted$fairness.vice) 
sum(data_moral_cruz_extracted$loyalty.vice) 
sum(data_moral_cruz_extracted$authority.vice) 
sum(data_moral_cruz_extracted$sanctity.vice) 
368/2393
232/2393
569/2393
456/2393
342/2393
257/2393
47/2393
35/2393
71/2393
52/2393

cruz_loyalty.virtue <- tokens_select(toks_cruz, pattern = extracted_dict$care.virtue_ex, valuetype = "glob")
cruz_loyalty.virtue <- as.character(cruz_loyalty.virtue)

#RUBIO
extracted_moral_toks_rubio <- tokens_select(toks_rubio, pattern = extracted_dict, valuetype = "glob")
rubio_moral_extracted <- as.character(extracted_moral_toks_rubio)
sum(ntoken(rubio_moral_extracted))

rubio_moral_dfm_extracted <- dfm(rubio_moral_extracted, remove_punct=TRUE)
rubio_moral_dfm_extracted <-dfm_weight(rubio_moral_dfm_extracted, scheme = "prop")

dict_moral_rubio_extracted <- dfm_lookup(rubio_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_rubio_extracted <- as.data.frame(dict_moral_rubio_extracted)

sum(data_moral_rubio_extracted$care.virtue)  
sum(data_moral_rubio_extracted$fairness.virtue) 
sum(data_moral_rubio_extracted$loyalty.virtue)  
sum(data_moral_rubio_extracted$authority.virtue) 
sum(data_moral_rubio_extracted$sanctity.virtue)  
sum(data_moral_rubio_extracted$care.vice)  
sum(data_moral_rubio_extracted$fairness.vice) 
sum(data_moral_rubio_extracted$loyalty.vice) 
sum(data_moral_rubio_extracted$authority.vice)  
sum(data_moral_rubio_extracted$sanctity.vice) 
207/826
38/826
172/826
189/826
107/826
99/826
6/826
6/826
9/826
10/826

rubio_loyalty.virtue <- tokens_select(toks_rubio, pattern = extracted_dict$care.virtue_ex, valuetype = "glob")
rubio_loyalty.virtue <- as.character(rubio_loyalty.virtue)

#KASICH
extracted_moral_toks_kasich <- tokens_select(toks_kasich, pattern = extracted_dict, valuetype = "glob")
extracted_moral_toks_kasich <- tokens_select(extracted_moral_toks_kasich, pattern = "help*", selection = "remove", valuetype = "glob")
kasich_moral_extracted <- as.character(extracted_moral_toks_kasich)
sum(ntoken(kasich_moral_extracted))

kasich_moral_dfm_extracted <- dfm(kasich_moral_extracted, remove_punct=TRUE)
kasich_moral_dfm_extracted <-dfm_weight(kasich_moral_dfm_extracted, scheme = "prop")

dict_moral_kasich_extracted <- dfm_lookup(kasich_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_kasich_extracted <- as.data.frame(dict_moral_kasich_extracted)

sum(data_moral_kasich_extracted$care.virtue)  
sum(data_moral_kasich_extracted$fairness.virtue)  
sum(data_moral_kasich_extracted$loyalty.virtue) 
sum(data_moral_kasich_extracted$authority.virtue)  
sum(data_moral_kasich_extracted$sanctity.virtue)  
sum(data_moral_kasich_extracted$care.vice)  
sum(data_moral_kasich_extracted$fairness.vice)  
sum(data_moral_kasich_extracted$loyalty.vice)  
sum(data_moral_kasich_extracted$authority.vice)   
sum(data_moral_kasich_extracted$sanctity.vice)  
120/739
18/739
215/739
216/739
56/739
81/739
3/739
6/739
4/739
29/739


kasich_loyalty.virtue <- tokens_select(extracted_moral_toks_kasich, pattern = extracted_dict$care.virtue_ex, valuetype = "glob")
kasich_loyalty.virtue <- as.character(kasich_loyalty.virtue)

#CARSON
extracted_moral_toks_carson <- tokens_select(toks_carson, pattern = extracted_dict, valuetype = "glob")
carson_moral_extracted <- as.character(extracted_moral_toks_carson)
sum(ntoken(carson_moral_extracted))

carson_moral_dfm_extracted <- dfm(carson_moral_extracted, remove_punct=TRUE)
carson_moral_dfm_extracted <-dfm_weight(carson_moral_dfm_extracted, scheme = "prop")

dict_moral_carson_extracted <- dfm_lookup(carson_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_carson_extracted <- as.data.frame(dict_moral_carson_extracted)

sum(data_moral_carson_extracted$care.virtue)  
sum(data_moral_carson_extracted$fairness.virtue)  
sum(data_moral_carson_extracted$loyalty.virtue) 
sum(data_moral_carson_extracted$authority.virtue)  
sum(data_moral_carson_extracted$sanctity.virtue) 
sum(data_moral_carson_extracted$care.vice)  
sum(data_moral_carson_extracted$fairness.vice)   
sum(data_moral_carson_extracted$loyalty.vice)  
sum(data_moral_carson_extracted$authority.vice) 
sum(data_moral_carson_extracted$sanctity.vice) 
144/785
62/785
240/785
120/785
128/785
71/785
7/785
8/785
13/785
9/785

carson_loyalty.virtue <- tokens_select(toks_carson, pattern = extracted_dict$loyalty.virtue_ex, valuetype = "glob")
carson_loyalty.virtue <- as.character(carson_loyalty.virtue)

#BUSH
extracted_moral_toks_bush <- tokens_select(toks_bush, pattern = extracted_dict, valuetype = "glob")
bush_moral_extracted <- as.character(extracted_moral_toks_bush)
sum(ntoken(bush_moral_extracted))

bush_moral_dfm_extracted <- dfm(bush_moral_extracted, remove_punct=TRUE)
bush_moral_dfm_extracted <-dfm_weight(bush_moral_dfm_extracted, scheme = "prop")

dict_moral_bush_extracted <- dfm_lookup(bush_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_bush_extracted <- as.data.frame(dict_moral_bush_extracted)

sum(data_moral_bush_extracted$care.virtue)  
sum(data_moral_bush_extracted$fairness.virtue)  
sum(data_moral_bush_extracted$loyalty.virtue) 
sum(data_moral_bush_extracted$authority.virtue) 
sum(data_moral_bush_extracted$sanctity.virtue)  
sum(data_moral_bush_extracted$care.vice)  
sum(data_moral_bush_extracted$fairness.vice)   
sum(data_moral_bush_extracted$loyalty.vice)  
sum(data_moral_bush_extracted$authority.vice)  
sum(data_moral_bush_extracted$sanctity.vice)  
168/941
48/941
196/941
235/941
104/941
145/941
9/941
6/941
26/941
30/941

bush_loyalty.virtue <- tokens_select(toks_bush, pattern = extracted_dict$loyalty.virtue_ex, valuetype = "glob")
bush_loyalty.virtue <- as.character(bush_loyalty.virtue)

#PAUL
extracted_moral_toks_paul <- tokens_select(toks_paul, pattern = extracted_dict, valuetype = "glob")
paul_moral_extracted <- as.character(extracted_moral_toks_paul)
sum(ntoken(paul_moral_extracted))

paul_moral_dfm_extracted <- dfm(paul_moral_extracted, remove_punct=TRUE)
paul_moral_dfm_extracted <-dfm_weight(paul_moral_dfm_extracted, scheme = "prop")

dict_moral_paul_extracted <- dfm_lookup(paul_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_paul_extracted <- as.data.frame(dict_moral_paul_extracted)

sum(data_moral_paul_extracted$care.virtue)  
sum(data_moral_paul_extracted$fairness.virtue)  
sum(data_moral_paul_extracted$loyalty.virtue)  
sum(data_moral_paul_extracted$authority.virtue) 
sum(data_moral_paul_extracted$sanctity.virtue)  
sum(data_moral_paul_extracted$care.vice)  
sum(data_moral_paul_extracted$fairness.vice)   
sum(data_moral_paul_extracted$loyalty.vice)  
sum(data_moral_paul_extracted$authority.vice)   
sum(data_moral_paul_extracted$sanctity.vice)  
397/1799
216/1799
430/1799
353/1799
69/1799
123/1799
29/1799
13/1799
120/1799
74/1799

paul_loyalty.virtue <- tokens_select(toks_paul, pattern = extracted_dict$loyalty.virtue_ex, valuetype = "glob")
paul_loyalty.virtue <- as.character(paul_loyalty.virtue)

#FIORINA
extracted_moral_toks_fiorina <- tokens_select(toks_fiorina, pattern = extracted_dict, valuetype = "glob")
fiorina_moral_extracted <- as.character(extracted_moral_toks_fiorina)
sum(ntoken(fiorina_moral_extracted))

fiorina_moral_dfm_extracted <- dfm(fiorina_moral_extracted, remove_punct=TRUE)
fiorina_moral_dfm_extracted <-dfm_weight(fiorina_moral_dfm_extracted, scheme = "prop")

dict_moral_fiorina_extracted <- dfm_lookup(fiorina_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_fiorina_extracted <- as.data.frame(dict_moral_fiorina_extracted)

sum(data_moral_fiorina_extracted$care.virtue)  
sum(data_moral_fiorina_extracted$fairness.virtue)  
sum(data_moral_fiorina_extracted$loyalty.virtue) 
sum(data_moral_fiorina_extracted$authority.virtue) 
sum(data_moral_fiorina_extracted$sanctity.virtue)
sum(data_moral_fiorina_extracted$care.vice) 
sum(data_moral_fiorina_extracted$fairness.vice)  
sum(data_moral_fiorina_extracted$loyalty.vice) 
sum(data_moral_fiorina_extracted$authority.vice)  
sum(data_moral_fiorina_extracted$sanctity.vice) 
122/453
31/453
165/453
66/453
19/453
29/453
6/453
6/453
7/453
5/453

fiorina_loyalty.virtue <- tokens_select(toks_fiorina, pattern = extracted_dict$loyalty.virtue_ex, valuetype = "glob")
fiorina_loyalty.virtue <- as.character(fiorina_loyalty.virtue)

#HUCKABEE
extracted_moral_toks_huckabee <- tokens_select(toks_huckabee, pattern = extracted_dict, valuetype = "glob")
huckabee_moral_extracted <- as.character(extracted_moral_toks_huckabee)
sum(ntoken(huckabee_moral_extracted))

huckabee_moral_dfm_extracted <- dfm(huckabee_moral_extracted, remove_punct=TRUE)
huckabee_moral_dfm_extracted <-dfm_weight(huckabee_moral_dfm_extracted, scheme = "prop")

dict_moral_huckabee_extracted <- dfm_lookup(huckabee_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_huckabee_extracted <- as.data.frame(dict_moral_huckabee_extracted)

sum(data_moral_huckabee_extracted$care.virtue) 
sum(data_moral_huckabee_extracted$fairness.virtue) 
sum(data_moral_huckabee_extracted$loyalty.virtue) 
sum(data_moral_huckabee_extracted$authority.virtue) 
sum(data_moral_huckabee_extracted$sanctity.virtue) 
sum(data_moral_huckabee_extracted$care.vice) 
sum(data_moral_huckabee_extracted$fairness.vice) 
sum(data_moral_huckabee_extracted$loyalty.vice) 
sum(data_moral_huckabee_extracted$authority.vice) 
sum(data_moral_huckabee_extracted$sanctity.vice) 
147/943
107/943
124/943
148/943
192/943
141/943
35/943
12/943
29/943
30/943

huckabee_fairness.vice <- tokens_select(extracted_moral_toks_huckabee, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
huckabee_fairness.vice <- as.character(huckabee_fairness.vice)

#WALKER
extracted_moral_toks_walker <- tokens_select(toks_walker, pattern = extracted_dict, valuetype = "glob")
walker_moral_extracted <- as.character(extracted_moral_toks_walker)
sum(ntoken(walker_moral_extracted))

walker_moral_dfm_extracted <- dfm(walker_moral_extracted, remove_punct=TRUE)
walker_moral_dfm_extracted <-dfm_weight(walker_moral_dfm_extracted, scheme = "prop")

dict_moral_walker_extracted <- dfm_lookup(walker_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_walker_extracted <- as.data.frame(dict_moral_walker_extracted)

sum(data_moral_walker_extracted$care.virtue) 
sum(data_moral_walker_extracted$fairness.virtue) 
sum(data_moral_walker_extracted$loyalty.virtue) 
sum(data_moral_walker_extracted$authority.virtue) 
sum(data_moral_walker_extracted$sanctity.virtue) 
sum(data_moral_walker_extracted$care.vice) 
sum(data_moral_walker_extracted$fairness.vice) 
sum(data_moral_walker_extracted$loyalty.vice) 
sum(data_moral_walker_extracted$authority.vice) 
sum(data_moral_walker_extracted$sanctity.vice) 
69/425
41/425
74/425
144/425
23/425
53/425
4/425
5/425
10/425
10/425

walker_fairness.vice <- tokens_select(extracted_moral_toks_walker, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
walker_fairness.vice <- as.character(walker_fairness.vice)

#GRAHAM
extracted_moral_toks_graham <- tokens_select(toks_graham, pattern = extracted_dict, valuetype = "glob")
graham_moral_extracted <- as.character(extracted_moral_toks_graham)
sum(ntoken(graham_moral_extracted))

graham_moral_dfm_extracted <- dfm(graham_moral_extracted, remove_punct=TRUE)
graham_moral_dfm_extracted <-dfm_weight(graham_moral_dfm_extracted, scheme = "prop")

dict_moral_graham_extracted <- dfm_lookup(graham_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_graham_extracted <- as.data.frame(dict_moral_graham_extracted)

sum(data_moral_graham_extracted$care.virtue) 
sum(data_moral_graham_extracted$fairness.virtue) 
sum(data_moral_graham_extracted$loyalty.virtue) 
sum(data_moral_graham_extracted$authority.virtue) 
sum(data_moral_graham_extracted$sanctity.virtue) 
sum(data_moral_graham_extracted$care.vice) 
sum(data_moral_graham_extracted$fairness.vice) 
sum(data_moral_graham_extracted$loyalty.vice) 
sum(data_moral_graham_extracted$authority.vice) 
sum(data_moral_graham_extracted$sanctity.vice) 
128/966
42/966
272/966
157/966
53/966
272/966
8/966
14/966
6/966
28/966

graham_fairness.vice <- tokens_select(extracted_moral_toks_graham, pattern = extracted_dict$care.vice_ex, valuetype = "glob")
graham_fairness.vice <- as.character(graham_fairness.vice)

#JINDAL
extracted_moral_toks_jindal <- tokens_select(toks_jindal, pattern = extracted_dict, valuetype = "glob")
jindal_moral_extracted <- as.character(extracted_moral_toks_jindal)
sum(ntoken(jindal_moral_extracted))

jindal_moral_dfm_extracted <- dfm(jindal_moral_extracted, remove_punct=TRUE)
jindal_moral_dfm_extracted <-dfm_weight(jindal_moral_dfm_extracted, scheme = "prop")

dict_moral_jindal_extracted <- dfm_lookup(jindal_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_jindal_extracted <- as.data.frame(dict_moral_jindal_extracted)

sum(data_moral_jindal_extracted$care.virtue) 
sum(data_moral_jindal_extracted$fairness.virtue) 
sum(data_moral_jindal_extracted$loyalty.virtue) 
sum(data_moral_jindal_extracted$authority.virtue) 
sum(data_moral_jindal_extracted$sanctity.virtue) 
sum(data_moral_jindal_extracted$care.vice) 
sum(data_moral_jindal_extracted$fairness.vice) 
sum(data_moral_jindal_extracted$loyalty.vice) 
sum(data_moral_jindal_extracted$authority.vice) 
sum(data_moral_jindal_extracted$sanctity.vice) 
102/421
33/421
52/421
81/421
78/421
42/421
11/421
6/421
16/421
9/421

jindal_fairness.vice <- tokens_select(extracted_moral_toks_jindal, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
jindal_fairness.vice <- as.character(jindal_fairness.vice)

#SANTORUM
extracted_moral_toks_santorum <- tokens_select(toks_santorum, pattern = extracted_dict, valuetype = "glob")
santorum_moral_extracted <- as.character(extracted_moral_toks_santorum)
sum(ntoken(santorum_moral_extracted))

santorum_moral_dfm_extracted <- dfm(santorum_moral_extracted, remove_punct=TRUE)
santorum_moral_dfm_extracted <-dfm_weight(santorum_moral_dfm_extracted, scheme = "prop")

dict_moral_santorum_extracted <- dfm_lookup(santorum_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_santorum_extracted <- as.data.frame(dict_moral_santorum_extracted)

sum(data_moral_santorum_extracted$care.virtue) 
sum(data_moral_santorum_extracted$fairness.virtue) 
sum(data_moral_santorum_extracted$loyalty.virtue) 
sum(data_moral_santorum_extracted$authority.virtue) 
sum(data_moral_santorum_extracted$sanctity.virtue) 
sum(data_moral_santorum_extracted$care.vice) 
sum(data_moral_santorum_extracted$fairness.vice) 
sum(data_moral_santorum_extracted$loyalty.vice) 
sum(data_moral_santorum_extracted$authority.vice) 
sum(data_moral_santorum_extracted$sanctity.vice) 
61/410
26/410
134/410
53/410
66/410
40/410
8/410
10/410
9/410
11/410

santorum_fairness.vice <- tokens_select(extracted_moral_toks_santorum, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
santorum_fairness.vice <- as.character(santorum_fairness.vice)

#PATAKI
extracted_moral_toks_pataki <- tokens_select(toks_pataki, pattern = extracted_dict, valuetype = "glob")
pataki_moral_extracted <- as.character(extracted_moral_toks_pataki)
sum(ntoken(pataki_moral_extracted))

pataki_moral_dfm_extracted <- dfm(pataki_moral_extracted, remove_punct=TRUE)
pataki_moral_dfm_extracted <-dfm_weight(pataki_moral_dfm_extracted, scheme = "prop")

dict_moral_pataki_extracted <- dfm_lookup(pataki_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_pataki_extracted <- as.data.frame(dict_moral_pataki_extracted)

sum(data_moral_pataki_extracted$care.virtue) 
sum(data_moral_pataki_extracted$fairness.virtue) 
sum(data_moral_pataki_extracted$loyalty.virtue) 
sum(data_moral_pataki_extracted$authority.virtue) 
sum(data_moral_pataki_extracted$sanctity.virtue) 
sum(data_moral_pataki_extracted$care.vice) 
sum(data_moral_pataki_extracted$fairness.vice) 
sum(data_moral_pataki_extracted$loyalty.vice) 
sum(data_moral_pataki_extracted$authority.vice) 
sum(data_moral_pataki_extracted$sanctity.vice) 
35/359
40/359
72/359
78/359
44/359
78/359
2/359
8/359
4/359
11/359

pataki_fairness.vice <- tokens_select(extracted_moral_toks_pataki, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
pataki_fairness.vice <- as.character(pataki_fairness.vice)
```
Step 14: Apply new "specific" dictionary to each 2016 DEMCRATIC PRIMARY candidate corpus
```{r}
#CLINTON
extracted_moral_toks_clinton_primary <- tokens_select(toks_clinton_2016primary, pattern = extracted_dict, valuetype = "glob")
clinton_primary_moral_extracted <- as.character(extracted_moral_toks_clinton_primary)
sum(ntoken(clinton_primary_moral_extracted))

clinton_primary_moral_dfm_extracted <- dfm(clinton_primary_moral_extracted, remove_punct=TRUE)
clinton_primary_moral_dfm_extracted <-dfm_weight(clinton_primary_moral_dfm_extracted, scheme = "prop")

dict_moral_clinton_primary_extracted <- dfm_lookup(clinton_primary_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_clinton_primary_extracted <- as.data.frame(dict_moral_clinton_primary_extracted)

sum(data_moral_clinton_primary_extracted$care.virtue) 
sum(data_moral_clinton_primary_extracted$fairness.virtue) 
sum(data_moral_clinton_primary_extracted$loyalty.virtue) 
sum(data_moral_clinton_primary_extracted$authority.virtue) 
sum(data_moral_clinton_primary_extracted$sanctity.virtue) 
sum(data_moral_clinton_primary_extracted$care.vice) 
sum(data_moral_clinton_primary_extracted$fairness.vice) 
sum(data_moral_clinton_primary_extracted$loyalty.vice) 
sum(data_moral_clinton_primary_extracted$authority.vice) 
sum(data_moral_clinton_primary_extracted$sanctity.vice) 
915/2953
533/2953
379/2953
244/2953
149/2953
499/2953
161/2953
6/2953
30/2953
96/2953


clinton_primary_fairness.vice <- tokens_select(extracted_moral_toks_clinton_primary, pattern = extracted_dict$care.virtue_ex, valuetype = "glob")
clinton_primary_fairness.vice <- as.character(clinton_primary_fairness.vice)

#sanders
extracted_moral_toks_sanders_primary <- tokens_select(toks_sanders_2016primary, pattern = extracted_dict, valuetype = "glob")
sanders_primary_moral_extracted <- as.character(extracted_moral_toks_sanders_primary)
sum(ntoken(sanders_primary_moral_extracted))

sanders_primary_moral_dfm_extracted <- dfm(sanders_primary_moral_extracted, remove_punct=TRUE)
sanders_primary_moral_dfm_extracted <-dfm_weight(sanders_primary_moral_dfm_extracted, scheme = "prop")

dict_moral_sanders_primary_extracted <- dfm_lookup(sanders_primary_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_sanders_primary_extracted <- as.data.frame(dict_moral_sanders_primary_extracted)

sum(data_moral_sanders_primary_extracted$care.virtue) 
sum(data_moral_sanders_primary_extracted$fairness.virtue) 
sum(data_moral_sanders_primary_extracted$loyalty.virtue) 
sum(data_moral_sanders_primary_extracted$authority.virtue) 
sum(data_moral_sanders_primary_extracted$sanctity.virtue) 
sum(data_moral_sanders_primary_extracted$care.vice) 
sum(data_moral_sanders_primary_extracted$fairness.vice) 
sum(data_moral_sanders_primary_extracted$loyalty.vice) 
sum(data_moral_sanders_primary_extracted$authority.vice) 
sum(data_moral_sanders_primary_extracted$sanctity.vice) 
1050/3587
370/3587
980/3587
400/3587
149/3587
304/3587
175/3587
1/3587
28/3587
197/3587

sanders_primary_fairness.vice <- tokens_select(extracted_moral_toks_sanders_primary, pattern = extracted_dict$care.virtue_ex, valuetype = "glob")
sanders_primary_fairness.vice <- as.character(sanders_primary_fairness.vice)

#O'MALLEY
extracted_moral_toks_omalley_primary <- tokens_select(toks_omalley_2016primary, pattern = extracted_dict, valuetype = "glob")
omalley_primary_moral_extracted <- as.character(extracted_moral_toks_omalley_primary)
sum(ntoken(omalley_primary_moral_extracted))

omalley_primary_moral_dfm_extracted <- dfm(omalley_primary_moral_extracted, remove_punct=TRUE)
omalley_primary_moral_dfm_extracted <-dfm_weight(omalley_primary_moral_dfm_extracted, scheme = "prop")

dict_moral_omalley_primary_extracted <- dfm_lookup(omalley_primary_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_omalley_primary_extracted <- as.data.frame(dict_moral_omalley_primary_extracted)

sum(data_moral_omalley_primary_extracted$care.virtue) 
sum(data_moral_omalley_primary_extracted$fairness.virtue) 
sum(data_moral_omalley_primary_extracted$loyalty.virtue) 
sum(data_moral_omalley_primary_extracted$authority.virtue) 
sum(data_moral_omalley_primary_extracted$sanctity.virtue) 
sum(data_moral_omalley_primary_extracted$care.vice) 
sum(data_moral_omalley_primary_extracted$fairness.vice) 
sum(data_moral_omalley_primary_extracted$loyalty.vice) 
sum(data_moral_omalley_primary_extracted$authority.vice) 
sum(data_moral_omalley_primary_extracted$sanctity.vice) 
244/985
147/985
175/985
211/985
110/985
68/985
24/985
2/985
0/985
18/985

omalley_primary_fairness.vice <- tokens_select(extracted_moral_toks_omalley_primary, pattern = extracted_dict$sanctity.virtue_ex, valuetype = "glob")
omalley_primary_fairness.vice <- as.character(omalley_primary_fairness.vice)
```
Step 15: Apply new "specific" dictionary to each 2016 & 2020 GENERAL ELECTION candidate corpus
```{r}
#TRUMP 2016
extracted_moral_toks_trump_moral2016GE <- tokens_select(toks_trump_2016GE, pattern = extracted_dict, valuetype = "glob")
extracted_moral_toks_trump_moral2016GE <- tokens_remove(extracted_moral_toks_trump_moral2016GE, pattern = c("crooked", "Crooked", "CROOKED"), valuetype = "glob")

trump_moral2016GE_moral_extracted <- as.character(extracted_moral_toks_trump_moral2016GE)
sum(ntoken(trump_moral2016GE_moral_extracted))

trump_moral2016GE_moral_dfm_extracted <- dfm(trump_moral2016GE_moral_extracted, remove_punct=TRUE)
trump_moral2016GE_moral_dfm_extracted <-dfm_weight(trump_moral2016GE_moral_dfm_extracted, scheme = "prop")

dict_moral_trump_moral2016GE_extracted <- dfm_lookup(trump_moral2016GE_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_trump_moral2016GE_extracted <- as.data.frame(dict_moral_trump_moral2016GE_extracted)

sum(data_moral_trump_moral2016GE_extracted$care.virtue) 
sum(data_moral_trump_moral2016GE_extracted$fairness.virtue) 
sum(data_moral_trump_moral2016GE_extracted$loyalty.virtue) 
sum(data_moral_trump_moral2016GE_extracted$authority.virtue) 
sum(data_moral_trump_moral2016GE_extracted$sanctity.virtue) 
sum(data_moral_trump_moral2016GE_extracted$care.vice) 
sum(data_moral_trump_moral2016GE_extracted$fairness.vice) 
sum(data_moral_trump_moral2016GE_extracted$loyalty.vice) 
sum(data_moral_trump_moral2016GE_extracted$authority.vice)
sum(data_moral_trump_moral2016GE_extracted$sanctity.vice) 
136/841
59/841
143/841
150/841
37/841
131/841
114/841
9/841
32/841
51/841

trump_moral2016GE_fairness.vice <- tokens_select(extracted_moral_toks_trump_moral2016GE, pattern = extracted_dict$care.vice_ex, valuetype = "glob")
trump_moral2016GE_fairness.vice <- as.character(trump_moral2016GE_fairness.vice)

#CLINTON 2016
extracted_moral_toks_clinton_moral2016GE <- tokens_select(toks_clinton_2016GE, pattern = extracted_dict, valuetype = "glob")
clinton_moral2016GE_moral_extracted <- as.character(extracted_moral_toks_clinton_moral2016GE)
sum(ntoken(clinton_moral2016GE_moral_extracted))

clinton_moral2016GE_moral_dfm_extracted <- dfm(clinton_moral2016GE_moral_extracted, remove_punct=TRUE)
clinton_moral2016GE_moral_dfm_extracted <-dfm_weight(clinton_moral2016GE_moral_dfm_extracted, scheme = "prop")

dict_moral_clinton_moral2016GE_extracted <- dfm_lookup(clinton_moral2016GE_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_clinton_moral2016GE_extracted <- as.data.frame(dict_moral_clinton_moral2016GE_extracted)

sum(data_moral_clinton_moral2016GE_extracted$care.virtue) 
sum(data_moral_clinton_moral2016GE_extracted$fairness.virtue) 
sum(data_moral_clinton_moral2016GE_extracted$loyalty.virtue) 
sum(data_moral_clinton_moral2016GE_extracted$authority.virtue) 
sum(data_moral_clinton_moral2016GE_extracted$sanctity.virtue)
sum(data_moral_clinton_moral2016GE_extracted$care.vice) 
sum(data_moral_clinton_moral2016GE_extracted$fairness.vice) 
sum(data_moral_clinton_moral2016GE_extracted$loyalty.vice) 
sum(data_moral_clinton_moral2016GE_extracted$authority.vice) 
sum(data_moral_clinton_moral2016GE_extracted$sanctity.vice) 
469/1850
227/1850
382/1850
246/1850
83/1850
285/1850
120/1850
4/1850
34/1850
42/1850

clinton_moral2016GE_fairness.vice <- tokens_select(extracted_moral_toks_clinton_moral2016GE, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
clinton_moral2016GE_fairness.vice <- as.character(clinton_moral2016GE_fairness.vice)

#TRUMP 2020
extracted_moral_toks_trump_moral2020GE <- tokens_select(toks_trump_2020GE, pattern = extracted_dict, valuetype = "glob")
trump_moral2020GE_moral_extracted <- as.character(extracted_moral_toks_trump_moral2020GE)
sum(ntoken(trump_moral2020GE_moral_extracted))

trump_moral2020GE_moral_dfm_extracted <- dfm(trump_moral2020GE_moral_extracted, remove_punct=TRUE)
trump_moral2020GE_moral_dfm_extracted <-dfm_weight(trump_moral2020GE_moral_dfm_extracted, scheme = "prop")

dict_moral_trump_moral2020GE_extracted <- dfm_lookup(trump_moral2020GE_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_trump_moral2020GE_extracted <- as.data.frame(dict_moral_trump_moral2020GE_extracted)

sum(data_moral_trump_moral2020GE_extracted$care.virtue) 
sum(data_moral_trump_moral2020GE_extracted$fairness.virtue) 
sum(data_moral_trump_moral2020GE_extracted$loyalty.virtue) 
sum(data_moral_trump_moral2020GE_extracted$authority.virtue) 
sum(data_moral_trump_moral2020GE_extracted$sanctity.virtue) 
sum(data_moral_trump_moral2020GE_extracted$care.vice) 
sum(data_moral_trump_moral2020GE_extracted$fairness.vice) 
sum(data_moral_trump_moral2020GE_extracted$loyalty.vice) 
sum(data_moral_trump_moral2020GE_extracted$authority.vice) 
sum(data_moral_trump_moral2020GE_extracted$sanctity.vice) 
951/5093
418/5093
810/5093
1015/5093
305/5093
566/5093
329/5093
63/5093
277/5093
476/5093

trump_moral2020GE_fairness.vice <- tokens_select(extracted_moral_toks_trump_moral2020GE, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
trump_moral2020GE_fairness.vice <- as.character(trump_moral2020GE_fairness.vice)

#BIDEN 2020
extracted_moral_toks_biden_moral2020GE <- tokens_select(toks_biden_2020GE, pattern = extracted_dict, valuetype = "glob")
biden_moral2020GE_moral_extracted <- as.character(extracted_moral_toks_biden_moral2020GE)
sum(ntoken(biden_moral2020GE_moral_extracted))

biden_moral2020GE_moral_dfm_extracted <- dfm(biden_moral2020GE_moral_extracted, remove_punct=TRUE)
biden_moral2020GE_moral_dfm_extracted <-dfm_weight(biden_moral2020GE_moral_dfm_extracted, scheme = "prop")

dict_moral_biden_moral2020GE_extracted <- dfm_lookup(biden_moral2020GE_moral_dfm_extracted, dictionary = data_dictionary_MFD)
data_moral_biden_moral2020GE_extracted <- as.data.frame(dict_moral_biden_moral2020GE_extracted)

sum(data_moral_biden_moral2020GE_extracted$care.virtue) 
sum(data_moral_biden_moral2020GE_extracted$fairness.virtue) 
sum(data_moral_biden_moral2020GE_extracted$loyalty.virtue) 
sum(data_moral_biden_moral2020GE_extracted$authority.virtue) 
sum(data_moral_biden_moral2020GE_extracted$sanctity.virtue) 
sum(data_moral_biden_moral2020GE_extracted$care.vice) 
sum(data_moral_biden_moral2020GE_extracted$fairness.vice) 
sum(data_moral_biden_moral2020GE_extracted$loyalty.vice) 
sum(data_moral_biden_moral2020GE_extracted$authority.vice) 
sum(data_moral_biden_moral2020GE_extracted$sanctity.vice) 
706/2567
246/2567
657/2567
222/2567
198/2567
261/2567
56/2567
7/2567
42/2567
200/2567

biden_moral2020GE_fairness.vice <- tokens_select(extracted_moral_toks_biden_moral2020GE, pattern = extracted_dict$fairness.vice_ex, valuetype = "glob")
biden_moral2020GE_fairness.vice <- as.character(biden_moral2020GE_fairness.vice)
```


EXPORT FILES OF WIEGHTED MORAL LANGAUGE 
Step 16: Write a new .txt file for the weighted moral language used by each 2020 DEMOCRATIC PRIMARY candidate 
```{r}
#BIDEN
toks_biden <- tokens(biden_corpus)
moral_toks_biden <- tokens_select(toks_biden, pattern = extracted_dict, valuetype = "glob")
biden_moral <- as.character(moral_toks_biden)
biden_moral <- paste0(biden_moral, collapse = ". ")
ntoken(biden_moral)
write(biden_moral, "biden_weighted_moral.txt")

#SANDERS
toks_sanders <- tokens(sanders_corpus)
moral_toks_sanders <- tokens_select(toks_sanders, pattern = extracted_dict, valuetype = "glob")
sanders_moral <- as.character(moral_toks_sanders)
sanders_moral <- paste0(sanders_moral, collapse = ". ")
ntoken(sanders_moral)
write(sanders_moral, "sanders_weighted_moral.txt")

#BUTTIGIEG
toks_buttigieg <- tokens(buttigieg_corpus)
moral_toks_buttigieg <- tokens_select(toks_buttigieg, pattern = extracted_dict, valuetype = "glob")
buttigieg_moral <- as.character(moral_toks_buttigieg)
buttigieg_moral <- paste0(buttigieg_moral, collapse = ". ")
ntoken(buttigieg_moral)
write(buttigieg_moral, "buttigieg_weighted_moral.txt")

#WARREN
toks_warren <- tokens(warren_corpus)
moral_toks_warren <- tokens_select(toks_warren, pattern = extracted_dict, valuetype = "glob")
warren_moral <- as.character(moral_toks_warren)
warren_moral <- paste0(warren_moral, collapse = ". ")
ntoken(warren_moral)
write(warren_moral, "warren_weighted_moral.txt")

#KLOBUCHAR
toks_klobuchar <- tokens(klobuchar_corpus)
moral_toks_klobuchar <- tokens_select(toks_klobuchar, pattern = extracted_dict, valuetype = "glob")
klobuchar_moral <- as.character(moral_toks_klobuchar)
klobuchar_moral <- paste0(klobuchar_moral, collapse = ". ")
ntoken(klobuchar_moral)
write(klobuchar_moral, "klobuchar_weighted_moral.txt")

#HARRIS
toks_harris <- tokens(harris_corpus)
moral_toks_harris <- tokens_select(toks_harris, pattern = extracted_dict, valuetype = "glob")
harris_moral <- as.character(moral_toks_harris)
harris_moral <- paste0(harris_moral, collapse = ". ")
ntoken(harris_moral)
write(harris_moral, "harris_weighted_moral.txt")

#YANG
toks_yang <- tokens(yang_corpus)
moral_toks_yang <- tokens_select(toks_yang, pattern = extracted_dict, valuetype = "glob")
yang_moral <- as.character(moral_toks_yang)
yang_moral <- paste0(yang_moral, collapse = ". ")
ntoken(yang_moral)
write(yang_moral, "yang_weighted_moral.txt")

#STEYER
toks_steyer <- tokens(steyer_corpus)
moral_toks_steyer <- tokens_select(toks_steyer, pattern = extracted_dict, valuetype = "glob")
steyer_moral <- as.character(moral_toks_steyer)
steyer_moral <- paste0(steyer_moral, collapse = ". ")
ntoken(steyer_moral)
write(steyer_moral, "steyer_weighted_moral.txt")

#BOOKER
toks_booker <- tokens(booker_corpus)
moral_toks_booker <- tokens_select(toks_booker, pattern = extracted_dict, valuetype = "glob")
booker_moral <- as.character(moral_toks_booker)
booker_moral <- paste0(booker_moral, collapse = ". ")
ntoken(booker_moral)
write(booker_moral, "booker_weighted_moral.txt")

#GABBARD
toks_gabbard <- tokens(gabbard_corpus)
moral_toks_gabbard <- tokens_select(toks_gabbard, pattern = extracted_dict, valuetype = "glob")
gabbard_moral <- as.character(moral_toks_gabbard)
gabbard_moral <- paste0(gabbard_moral, collapse = ". ")
ntoken(gabbard_moral)
write(gabbard_moral, "gabbard_weighted_moral.txt")

#CASTRO
toks_castro <- tokens(castro_corpus)
moral_toks_castro <- tokens_select(toks_castro, pattern = extracted_dict, valuetype = "glob")
castro_moral <- as.character(moral_toks_castro)
castro_moral <- paste0(castro_moral, collapse = ". ")
ntoken(castro_moral)
write(castro_moral, "castro_weighted_moral.txt")

#OROURKE
toks_orourke <- tokens(orourke_corpus)
moral_toks_orourke <- tokens_select(toks_orourke, pattern = extracted_dict, valuetype = "glob")
orourke_moral <- as.character(moral_toks_orourke)
orourke_moral <- paste0(orourke_moral, collapse = ". ")
ntoken(orourke_moral)
write(orourke_moral, "orourke_weighted_moral.txt")

#BENNET
toks_bennet <- tokens(bennet_corpus)
moral_toks_bennet <- tokens_select(toks_bennet, pattern = extracted_dict, valuetype = "glob")
bennet_moral <- as.character(moral_toks_bennet)
bennet_moral <- paste0(bennet_moral, collapse = ". ")
ntoken(bennet_moral)
write(bennet_moral, "bennet_weighted_moral.txt")

#DELANEY
toks_delaney <- tokens(delaney_corpus)
moral_toks_delaney <- tokens_select(toks_delaney, pattern = extracted_dict, valuetype = "glob")
delaney_moral <- as.character(moral_toks_delaney)
delaney_moral <- paste0(delaney_moral, collapse = ". ")
ntoken(delaney_moral)
write(delaney_moral, "delaney_weighted_moral.txt")

#WILLIAMSON
toks_williamson <- tokens(williamson_corpus)
moral_toks_williamson <- tokens_select(toks_williamson, pattern = extracted_dict, valuetype = "glob")
williamson_moral <- as.character(moral_toks_williamson)
williamson_moral <- paste0(williamson_moral, collapse = ". ")
ntoken(williamson_moral)
write(williamson_moral, "williamson_weighted_moral.txt")

#RYAN
toks_ryan <- tokens(ryan_corpus)
moral_toks_ryan <- tokens_select(toks_ryan, pattern = extracted_dict, valuetype = "glob")
ryan_moral <- as.character(moral_toks_ryan)
ryan_moral <- paste0(ryan_moral, collapse = ". ")
ntoken(ryan_moral)
write(ryan_moral, "ryan_weighted_moral.txt")

#GILLIBRAND
toks_gillibrand <- tokens(gillibrand_corpus)
moral_toks_gillibrand <- tokens_select(toks_gillibrand, pattern = extracted_dict, valuetype = "glob")
gillibrand_moral <- as.character(moral_toks_gillibrand)
gillibrand_moral <- paste0(gillibrand_moral, collapse = ". ")
ntoken(gillibrand_moral)
write(gillibrand_moral, "gillibrand_weighted_moral.txt")

#INSLEE
toks_inslee <- tokens(inslee_corpus)
moral_toks_inslee <- tokens_select(toks_inslee, pattern = extracted_dict, valuetype = "glob")
inslee_moral <- as.character(moral_toks_inslee)
inslee_moral <- paste0(inslee_moral, collapse = ". ")
ntoken(inslee_moral)
write(inslee_moral, "inslee_weighted_moral.txt")

#HICKENLOOPER
toks_hickenlooper <- tokens(hickenlooper_corpus)
moral_toks_hickenlooper <- tokens_select(toks_hickenlooper, pattern = extracted_dict, valuetype = "glob")
hickenlooper_moral <- as.character(moral_toks_hickenlooper)
hickenlooper_moral <- paste0(hickenlooper_moral, collapse = ". ")
ntoken(hickenlooper_moral)
write(hickenlooper_moral, "hickenlooper_weighted_moral.txt")

#BULLOCK
toks_bullock <- tokens(bullock_corpus)
moral_toks_bullock <- tokens_select(toks_bullock, pattern = extracted_dict, valuetype = "glob")
bullock_moral <- as.character(moral_toks_bullock)
bullock_moral <- paste0(bullock_moral, collapse = ". ")
ntoken(bullock_moral)
write(bullock_moral, "bullock_weighted_moral.txt")

#SWALWELL
toks_swalwell <- tokens(swalwell_corpus)
moral_toks_swalwell <- tokens_select(toks_swalwell, pattern = extracted_dict, valuetype = "glob")
swalwell_moral <- as.character(moral_toks_swalwell)
swalwell_moral <- paste0(swalwell_moral, collapse = ". ")
ntoken(swalwell_moral)
write(swalwell_moral, "swalwell_weighted_moral.txt")
```
Step 17: Write a new .txt file for the weighted moral language used by each 2016 REPUBLICAN PRIMARY candidate 
```{r}
#TRUMP
#create tokens object from trump corpus 
toks_trump <- tokens(trump_corpus)

#select dictionary matches
moral_toks_trump <- tokens_select(toks_trump, pattern = extracted_dict, valuetype = "glob")

#convert to character string & concatenate :)
trump_moral <- as.character(moral_toks_trump)
trump_moral <- paste0(trump_moral, collapse = ". ")

#check how many dictionary matches, and then write to a .txt file
ntoken(trump_moral)
write(trump_moral, "trump_weighted_moral.txt")

#CRUZ
toks_cruz <- tokens(cruz_corpus)
moral_toks_cruz <- tokens_select(toks_cruz, pattern = extracted_dict, valuetype = "glob")
cruz_moral <- as.character(moral_toks_cruz)
cruz_moral <- paste0(cruz_moral, collapse = ". ")
ntoken(cruz_moral)
write(cruz_moral, "cruz_weighted_moral.txt")

#RUBIO
toks_rubio <- tokens(rubio_corpus)
moral_toks_rubio <- tokens_select(toks_rubio, pattern = extracted_dict, valuetype = "glob")
rubio_moral <- as.character(moral_toks_rubio)
rubio_moral <- paste0(rubio_moral, collapse = ". ")
ntoken(rubio_moral)
write(rubio_moral, "rubio_weighted_moral.txt")

#KASICH
toks_kasich <- tokens(kasich_corpus)
moral_toks_kasich <- tokens_select(toks_kasich, pattern = extracted_dict, valuetype = "glob")
kasich_moral <- as.character(moral_toks_kasich)
kasich_moral <- paste0(kasich_moral, collapse = ". ")
ntoken(kasich_moral)
write(kasich_moral, "kasich_weighted_moral.txt")

#CARSON
toks_carson <- tokens(carson_corpus)
moral_toks_carson <- tokens_select(toks_carson, pattern = extracted_dict, valuetype = "glob")
carson_moral <- as.character(moral_toks_carson)
carson_moral <- paste0(carson_moral, collapse = ". ")
ntoken(carson_moral)
write(carson_moral, "carson_weighted_moral.txt")

#BUSH
toks_bush <- tokens(bush_corpus)
moral_toks_bush <- tokens_select(toks_bush, pattern = extracted_dict, valuetype = "glob")
bush_moral <- as.character(moral_toks_bush)
bush_moral <- paste0(bush_moral, collapse = ". ")
ntoken(bush_moral)
write(bush_moral, "bush_weighted_moral.txt")

#CHRISTIE
toks_christie <- tokens(christie_corpus)
moral_toks_christie <- tokens_select(toks_christie, pattern = extracted_dict, valuetype = "glob")
christie_moral <- as.character(moral_toks_christie)
christie_moral <- paste0(christie_moral, collapse = ". ")
ntoken(christie_moral)
write(christie_moral, "christie_weighted_moral.txt")

#PAUL
toks_paul <- tokens(paul_corpus)
moral_toks_paul <- tokens_select(toks_paul, pattern = extracted_dict, valuetype = "glob")
paul_moral <- as.character(moral_toks_paul)
paul_moral <- paste0(paul_moral, collapse = ". ")
ntoken(paul_moral)
write(paul_moral, "paul_weighted_moral.txt")

#FIORINA
toks_fiorina <- tokens(fiorina_corpus)
moral_toks_fiorina <- tokens_select(toks_fiorina, pattern = extracted_dict, valuetype = "glob")
fiorina_moral <- as.character(moral_toks_fiorina)
fiorina_moral <- paste0(fiorina_moral, collapse = ". ")
ntoken(fiorina_moral)
write(fiorina_moral, "fiorina_weighted_moral.txt")

#HUCKABEE
toks_huckabee <- tokens(huckabee_corpus)
moral_toks_huckabee <- tokens_select(toks_huckabee, pattern = extracted_dict, valuetype = "glob")
huckabee_moral <- as.character(moral_toks_huckabee)
huckabee_moral <- paste0(huckabee_moral, collapse = ". ")
ntoken(huckabee_moral)
write(huckabee_moral, "huckabee_weighted_moral.txt")

#WALKER
toks_walker <- tokens(walker_corpus)
moral_toks_walker <- tokens_select(toks_walker, pattern = extracted_dict, valuetype = "glob")
walker_moral <- as.character(moral_toks_walker)
walker_moral <- paste0(walker_moral, collapse = ". ")
ntoken(walker_moral)
write(walker_moral, "walker_weighted_moral.txt")

#GRAHAM
toks_graham <- tokens(graham_corpus)
moral_toks_graham <- tokens_select(toks_graham, pattern = extracted_dict, valuetype = "glob")
graham_moral <- as.character(moral_toks_graham)
graham_moral <- paste0(graham_moral, collapse = ". ")
ntoken(graham_moral)
write(graham_moral, "graham_weighted_moral.txt")

#JINDAL
toks_jindal <- tokens(jindal_corpus)
moral_toks_jindal <- tokens_select(toks_jindal, pattern = extracted_dict, valuetype = "glob")
jindal_moral <- as.character(moral_toks_jindal)
jindal_moral <- paste0(jindal_moral, collapse = ". ")
ntoken(jindal_moral)
write(jindal_moral, "jindal_weighted_moral.txt")

#SANTORUM
toks_santorum <- tokens(santorum_corpus)
moral_toks_santorum <- tokens_select(toks_santorum, pattern = extracted_dict, valuetype = "glob")
santorum_moral <- as.character(moral_toks_santorum)
santorum_moral <- paste0(santorum_moral, collapse = ". ")
ntoken(santorum_moral)
write(santorum_moral, "santorum_weighted_moral.txt")

#PATAKI
toks_pataki <- tokens(pataki_corpus)
moral_toks_pataki <- tokens_select(toks_pataki, pattern = extracted_dict, valuetype = "glob")
pataki_moral <- as.character(moral_toks_pataki)
pataki_moral <- paste0(pataki_moral, collapse = ". ")
ntoken(pataki_moral)
write(pataki_moral, "pataki_weighted_moral.txt")
```
Step 18: Write a new .txt file for the weighted moral language used by each 2016 DEMOCRATIC PRIMARY candidate
```{r}
#CLINTON
toks_clinton_2016primary <- tokens(clinton2016primary_corpus)
moral_toks_clinton_2016primary <- tokens_select(toks_clinton_2016primary, pattern = extracted_dict, valuetype = "glob")
clinton_2016primary_moral <- as.character(moral_toks_clinton_2016primary)
clinton_2016primary_moral <- paste0(clinton_2016primary_moral, collapse = ". ")
ntoken(clinton_2016primary_moral)
write(clinton_2016primary_moral, "clinton_2016primary_weighted_moral.txt")

#SANDERS
toks_sanders_2016primary <- tokens(sanders2016primary_corpus)
moral_toks_sanders_2016primary <- tokens_select(toks_sanders_2016primary, pattern = extracted_dict, valuetype = "glob")
sanders_2016primary_moral <- as.character(moral_toks_sanders_2016primary)
sanders_2016primary_moral <- paste0(sanders_2016primary_moral, collapse = ". ")
ntoken(sanders_2016primary_moral)
write(sanders_2016primary_moral, "sanders_2016primary_weighted_moral.txt")

#OMALLEY
toks_omalley_2016primary <- tokens(omalley2016primary_corpus)
moral_toks_omalley_2016primary <- tokens_select(toks_omalley_2016primary, pattern = extracted_dict, valuetype = "glob")
omalley_2016primary_moral <- as.character(moral_toks_omalley_2016primary)
omalley_2016primary_moral <- paste0(omalley_2016primary_moral, collapse = ". ")
ntoken(omalley_2016primary_moral)
write(omalley_2016primary_moral, "omalley_2016primary_weighted_moral.txt")
```
Step 19: Write a new .txt file for the weighted moral language used by each 2016 & 2020 GENERAL ELECTION candidate
```{r}
#CLINTON 2016 
toks_clinton_2016GE <- tokens(clinton2016_GE_corpus)
moral_toks_clinton_2016GE <- tokens_select(toks_clinton_2016GE, pattern = extracted_dict, valuetype = "glob")
clinton_2016GE_moral <- as.character(moral_toks_clinton_2016GE)
clinton_2016GE_moral <- paste0(clinton_2016GE_moral, collapse = ". ")
ntoken(clinton_2016GE_moral)
write(clinton_2016GE_moral, "clinton_2016GE_weighted_moral.txt")

#TRUMP 2016
toks_trump_2016GE <- tokens(trump2016_GE_corpus)
moral_toks_trump_2016GE <- tokens_select(toks_trump_2016GE, pattern = extracted_dict, valuetype = "glob")
trump_2016GE_moral <- as.character(moral_toks_trump_2016GE)
trump_2016GE_moral <- paste0(trump_2016GE_moral, collapse = ". ")
ntoken(trump_2016GE_moral)
write(trump_2016GE_moral, "trump_2016GE_weighted_moral.txt")

#BIDEN 2020
toks_biden_2020GE <- tokens(biden2020_GE_corpus)
moral_toks_biden_2020GE <- tokens_select(toks_biden_2020GE, pattern = extracted_dict, valuetype = "glob")
biden_2020GE_moral <- as.character(moral_toks_biden_2020GE)
biden_2020GE_moral <- paste0(biden_2020GE_moral, collapse = ". ")
ntoken(biden_2020GE_moral)
write(biden_2020GE_moral, "biden_2020GE_weighted_moral.txt")

#TRUMP 2020
toks_trump_2020GE <- tokens(trump2020_GE_corpus)
moral_toks_trump_2020GE <- tokens_select(toks_trump_2020GE, pattern = extracted_dict, valuetype = "glob")
trump_2020GE_moral <- as.character(moral_toks_trump_2020GE)
trump_2020GE_moral <- paste0(trump_2020GE_moral, collapse = ". ")
ntoken(trump_2020GE_moral)
write(trump_2020GE_moral, "trump_2020GE_weighted_moral.txt")
```

```{r}

```

